\documentclass[11pt, letterpaper, roman]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{banking} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
\usepackage[leftmargin=20pt]{etaremune}
\usepackage{multicol}
\usepackage[margin = 1in, paperheight=11in, paperwidth=8.5in]{geometry}

% Page Number
\usepackage{lastpage}
\pagestyle{fancy}
\fancyfoot[R]{\thepage\ / \pageref{LastPage}}

% New Commands
\newcommand{\workspace}{\vspace{3pt}}
\newcommand{\grantspace}{\vspace{-1pt}}
\newcommand{\awardspace}{\vspace{-2pt}}
\newcommand{\professionalspace}{\vspace{8pt}}
\newcommand{\leadershipspace}{\vspace{5pt}}
\newcommand{\outreachspace}{\vspace{5pt}}

\firstname{Claire}
\familyname{Bowen}
\lfoot{CLAIRE MCKAY BOWEN}

\begin{document}
\vspace{-10pt}
\centerline{\huge{CLAIRE MCKAY BOWEN}}
\vspace{10pt}
\hrule
\vspace{5pt}
\centerline{\small Email: cbowen@urban.org | Website: \href{https://www.clairemckaybowen.com}{www.clairemckaybowen.com} | Last Updated: \today}
\vspace{5pt}
\hrule

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \vspace{5pt}
\section{Education}
\cventry{}{Ph.D. Applied and Computational Mathematics and Statistics (ACMS)}{University of Notre Dame \textnormal{- Notre Dame, IN}}{\textnormal{\textit{May 2018}}}{}{
\underline{Advisor}: \href{http://acms.nd.edu/people/faculty/fang-liu/}{Dr. Fang Liu}\\
\underline{Dissertation Topic}: Data Privacy via Integration of Differential Privacy and Data Synthesis}

\vspace{2pt}
\cventry{}{M.S. Applied and Computational Mathematics and Statistics | GPA: 3.91/4.00}{University of Notre Dame \textnormal{- Notre Dame, IN}}{\textnormal{\textit{May 2015}}}{}{}
%\subsection{Relevant Coursework}
%\cvlistdoubleitem{Applied Linear Models I \& II}{Generalized Linear Models}
%\cvlistdoubleitem{Applied Probability}{Statistical Methods in Data Mining}
%\cvlistdoubleitem{Bayesian Statistics}{Statistics in the Computer Era (Bootstrap)}

\vspace{2pt}
\cventry{}{Honors B.S. Mathematics and Physics | Minor: Statistics | High Honors: Top 5\% | GPA: 3.94/4.00}{Idaho State University \textnormal{- Pocatello, ID}}{\textnormal{\hspace{-25pt}\textit{Dec. 2012}}}{}{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Research Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-10pt}
\section{Professional Experience}
    \textbf{Urban Institute} \hfill \textit{Dec. 2019 - Present}\\
    \textit{Principal Research Associate and Statistical Methods Group Lead \hfill Oct. 2021 - Present}\\
    \textit{Lead Data Scientist, Privacy and Data Security \hfill Dec. 2019 - Sept. 2021}
    % \cventry{}{Lead Data Scientist, Privacy and Data Security}{Urban Institute}{\textnormal{\textit{Dec. 2019 - Present}}}{}{
    % \begin{itemize}
    %     \item Co-leading a multi-year project with the IRS to create synthetic versions of the income tax return database, assess the quality and privacy guarantee of the generated synthetic data, and develop methods for researchers to access confidential administrative data safely and securely.
    %    \item Developing a set of data privacy tools and communication materials to improve access to disaggregated data for city governments.
    %    \item Creating training materials on implementing synthetic data and differentially private methods for the Bureau of Economic Analysis
    %     \item Designing an interactive dashboard to assess and evaluate the 2020 Decennial Census population results in collaboration with Georgetown University Massive Data Institute.
    %     \item Creating a set of tools and resources on how to virtually teach kids about data, data science, and data visualization.
    %     \item Developing a body of work on data privacy and confidentiality communications.
    %     \item Managed a data privacy project on generating synthetic data on employer and employee industry data in rural communities in collaboration with the Bureau of Labor Statistics.
    % \end{itemize}'
    % }

\workspace
    \textbf{Stonehill College - School of Business} \hfill \textit{June 2022 - Present}\\
    \textit{Adjunct Professor}

\workspace
    \cventry{}{Postdoctoral Research Associate}{Los Alamos National Laboratory (LANL) - Los Alamos, NM}{\textnormal{\textit{\hspace{-1.5cm}June 2018 - Dec. 2019}}}{\underline{Advisors}: \href{http://www.lanl.gov/expertise/profiles/view/joanne-wendelberger}{Dr. Joanne Wendelberger and Dr. Earl Lawrence}}
    {}
    {
    % \begin{itemize}
    %     \item Evaluated various differentially private data synthesis methods and quality metric algorithms to assess practical applications, resulting in a journal publication.
    %     \item Developed new methods of functional data analysis, human-in-the-loop, and uncertainty quantification for iterative design problems.
    %     \item Investigated the reliability of computer hardware such as cosmic ray effects on supercomputers, resulting in a journal publication.
    %     \item Analyzed and evaluated Texas Pre-K to college longitudinal education data to identify attributes for success.
    %     % \item Explored and improved component reliability modeling within a Bayesian Framework.
    % \end{itemize}
    }

\workspace
    \textbf{University of Notre Dame - Notre Dame, IN, Dept. of ACMS} \hfill \textit{Aug. 2013 - May 2018}\\
    \textit{Graduate Research Assistant, \underline{Advisor}: \href{http://acms.nd.edu/people/faculty/fang-liu/}{Dr. Fang Liu} \hfill Aug. 2013 - May 2018}\\
    \textit{Probability and Statistics Instructor \hfill Jan. 2015 - May 2015}

\workspace
    \cventry{}{Graduate Research Assistant}{U.S. Census Bureau - Suitland, MD}{\textnormal{\textit{Aug. 2016 - Oct. 2016}}}{\underline{Advisors}: Dr. Tommy Wright and Dr. Martin Klein}
    {
    % \begin{itemize}
    %     \item Implemented methods of data privacy and confidentiality to U.S. Census Bureau data; specifically, applying model-based differentially private data synthesis methods.
    % % \item Awarded the opportunity to intern at the U.S. Census Bureau through the National Science Foundation Graduate Research Internship Program.
    % \end{itemize}
    }
% \vspace{4pt}
%     \cventry{}{Office of Grants and Fellowships Consultant}{University of Notre Dame - Notre Dame, IN, Graduate School}{\textnormal{\textit{July 2014 - May 2016}}}{}
%     {
%     % \begin{itemize}
%     %     \item Successfully advised several NSF GRFP winners from various STEM fields.
%     % \end{itemize}
%     }

\workspace
    \cventry{}{Graduate Research Assistant}{Los Alamos National Laboratory - Los Alamos, NM}{\textnormal{\textit{May 2015 - July 2015}}}{\underline{Advisor}:  \href{http://www.lanl.gov/expertise/profiles/view/joanne-wendelberger}{Dr. Joanne Wendelberger}}
    {
    %  and \href{http://www.lanl.gov/expertise/profiles/view/lawrence-ticknor}{Mr. Lawrence Ticknor}
    % \begin{itemize}
    %     \item Improved an in situ method for approximating complex computer simulations, resulting in a publication. 
    % % (publication \#3).
    %     \item Created a R package and Shiny App of the developed method as additional learning tools for researchers.
    % \end{itemize}
    }
    
\workspace
    \cventry{}{Graduate Research Assistant}{Indiana University of Health - Goshen, IN Center for Cancer Care}{\textnormal{\textit{Jan. 2014 - Nov. 2014}}}{\underline{Advisor}: \href{http://iuhealth.org/find-a-doctor/physician/69771/}{Dr. James A. Wheeler}}
    {
    % \begin{itemize}
    %     \item Wrote programs in R to investigate clinical data sets using survival analysis, resulting in a publication.
    % % (publication \#2).
    %     \item Created R Shiny Online Applications as an additional learning tool for published paper.
    % \end{itemize}
    }
    
\workspace
    \textbf{Idaho State University - Pocatello, ID, Dept. of Physics} \hfill \textit{Sept. 2010 - May 2013}\\
    \textit{Physics Proctor and Grader \hfill Sept. 2012 - May 2013}\\
    \textit{Laboratory Physics Teaching Assistant \hfill Jan. 2011 - May 2013}\\
    \textit{Physics Tutor \hfill Sept. 2010 - May. 2013}
    
\workspace
    \textbf{University of Illinois - Urbana-Champagne, IL, Dept. of Physics} \hfill \textit{Summers of 2011 and 2012}\\
    \textit{Undergraduate Research Assistant, \underline{Advisor}: Dr. Jose Mestre \hfill May 2012 - Aug. 2012}\\
    \textit{Research Experience for Undergraduate Researcher, \underline{Advisor}: Dr. Taekjip Ha \hfill May 2011 - Aug. 2011}

\workspace
    \cventry{}{\href{http://www.int.washington.edu/REU/2010/2010_photos.html}{Research Experience for Undergraduate Researcher}}{University of Washington - Seattle, WA, Dept. of Physics}{\textnormal{\textit{May 2010 - Aug. 2010}}}{\underline{Advisor}: Dr. Peter Shaffer}
    {
    % \begin{itemize}
    % \item Conducted statistical analysis on student response data to discover student misconceptions on physics topics through \textit{Tutorials in Introductory Physics} book, improving student understanding by more than 10\%.
    % \end{itemize}
    }

\workspace
    \cventry{}{Laboratory Technician}{Idaho State University - Pocatello, ID, Environmental Monitoring Lab}{\textnormal{\textit{May 2008 - May 2010}}}{}
    {
    % \begin{itemize}
    % \item Monitored Idaho National Laboratory's radiation emissions in the environment, performing these analyses:
    % \begin{itemize}
    % \item Gross alpha and beta analysis of air particulate filters and water samples on proportional counters.
    % \item Gamma-emitting radionuclides of charcoal, air particulate filters, and water on gamma spectrometers.
    % \item Tritium and low level tritium on liquid scintillation counter.
    % \end{itemize}
    % \end{itemize}
    }
    
% \newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Grants
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-30pt}
\section{Grants}
    \cventry{}{Economic Institutions, Behavior, and Performance | Grant No: G-2022-17149 | \$500,000}{Alfred P. Sloan Foundation}{\textnormal{\hspace{-1.5cm}\textit{May 2022 - April 2025}}}{}
    { 
        \underline{Project:} Build and Improve Synthetic Datasets Based on Administrative Tax Data\\
        \underline{Role:} Principal Investigator
    }
    
\grantspace   
     \cventry{}{NSF National Center for Science and Engineering Statistics | \$1.5 million}{National Science Foundation}{\textnormal{\textit{April 2022 - March 2025}}}{}
    {
        \underline{Project:} Building a Validation Server for Administrative Tax Data | 
        \underline{Role:} Principal Investigator
        % PI: Claire McKay Bowen, Co-PIs: Leonard Burman and Graham MacDonald
    }

\grantspace   
    \cventry{}{Regional Income Division | \$250,000}{Bureau of Economic Analysis}{\textnormal{\textit{Sept. 2021 - Dec. 2022}}}{}
    {
        Data Privacy Education Materials and Training | 
        \underline{Role:} Principal Investigator
        % PI: Claire McKay Bowen, Co-PI: Aaron R. Williams
    }

\grantspace 
    \cventry{}{Gates Foundation | \$150,000}{Gates Foundation}{\textnormal{\textit{Oct. 2021 - Nov. 2022}}}{}
    {
        \underline{Project:} Disaggregating Local Data without Privacy Harms | 
        \underline{Role:} Co-Principal Investigator
        % Co-PIs: Claire McKay Bowen, Ajjit Narayanan, and Alena Stern
    }

\grantspace    
    \cventry{}{Economic Institutions, Behavior, and Performance | Grant No: G-2020-14024 | \$400,000}{Alfred P. Sloan Foundation}{\textnormal{\hspace{-1.5cm}\textit{Nov. 2020 - Oct. 2022}}}{}
    { 
        \underline{Project:}  Development and Deployment of a Prototype Validation Server for Administrative Tax Data\\
        \underline{Role:} Principal Investigator
        % PI: Claire McKay Bowen, 
        % Co-PIs: Leonard Burman and Graham MacDonald
    }

\grantspace   
    \cventry{}{Urban Institute | \$5,000}{Seed Funding}{\textnormal{\textit{Sept. 2021 - Dec. 2021}}}{}
    {
        \underline{Project:} Urban Formatting for LaTeX | 
        \underline{Role:} Co-Principal Investigator
        % Co-PIs: Claire McKay Bowen and Alexandra Tammaro
    }

\grantspace  
    \cventry{}{South Big Data Hub | \$50,000}{South Big Data Hub Seed Grant}{\textnormal{\textit{May 2021 - Dec. 2021}}}{}
    {
        \underline{Project:} Data4Kids: Virtually Teaching Kids about Data Science | 
        \underline{Role:} Co-Principal Investigator
        % PI: Jonathan Schwabish, Co-PI: Claire McKay Bowen
    }

\grantspace 
    \cventry{}{Tableau Foundation | \$470,000}{Tableau and Salesforce}{\textnormal{\textit{Jan. 2021 - Dec. 2021}}}{}
    {
        \underline{Project:} Decennial Dashboard | 
        \underline{Role:} Co-Principal Investigator
        % Co-PIs: Claire McKay Bowen and Amy O'Hara
    }

\grantspace 
    \cventry{}{NSF National Center for Science and Engineering Statistics | \$600,000}{National Science Foundation}{\textnormal{\textit{Oct. 2020 - Sept. 2021}}}{}
    {
        \underline{Project:} Development and Deployment of a Prototype Validation Server for Administrative Tax Data\\
        \underline{Role:} Principal Investigator
        % PI: Claire McKay Bowen, Co-PIs: Leonard Burman and Graham MacDonald
    }

\grantspace 
    \cventry{}{Urban Institute | \$25,000}{Fleishman Innovation Award}{\textnormal{\textit{May 2020 - Dec. 2020}}}{}
    {
        \underline{Project:} Optimizing Data to Advance Rural Economic Development | 
        \underline{Role:} Co-Principal Investigator
        % Co-PIs: Claire McKay Bowen, Ajjit Narayanan, and Corianne Scally 
    }

\grantspace 
    \cventry{}{NIST Public Safety Communications Research | \$100,000}{National Institute of Standards and Technology (NIST)}{\textnormal{\textit{Oct. 2019 - Jan. 2020}}}{}
    {
        \underline{Project:} Comparative Study of Differentially Private Synthetic Data Algorithms and Evaluation Standards\\
        \underline{Role:} Principal Investigator
        % PI: Claire McKay Bowen
    }
    
% \newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Fellowships
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Fellowships}
    \cventry{}{National Science Foundation | \$5,000}{National Science Foundation Graduate Research Internship Program}{\textnormal{\textit{May 2016}}}{}{}
\awardspace
    \cventry{}{National Science Foundation | Grant No. DGE-1313583 | \$138,000}{National Science Foundation Graduate Research Fellowship}{\textnormal{\textit{May 2015}}}{}{}
\awardspace
    \cventry{}{Microsoft | \$17,000}{Microsoft Graduate Women's Fellowship}{\textnormal{\textit{Feb. 2014}}}{}{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Honors and Awards
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-10pt}

\section{Honors \& Awards}
    \cventry{}{Urban Institute}{2021 President's Award for Research Innovation}{\textnormal{\textit{April 2022}}}{}
    {
        % Development and Deployment of a Prototype Validation Server for Administrative Tax Data; Synthetic Supplemental Public Use File of Low-Income Information Return Data
    }
\awardspace
    \cventry{}{Committee of Presidents of Statistical Societies}{Committee of Presidents of Statistical Societies Leadership Academy}{\textnormal{\textit{Aug. 2021}}}{}{}
\awardspace
    \cventry{}{Urban Institute}{2020 President's Award for Entrepreneurship}{\textnormal{\textit{April 2021}}}{}
    {
        % Development and Deployment of a Prototype Validation Server for Administrative Tax Data; Synthetic Supplemental Public Use File of Low-Income Information Return Data
    }
\awardspace
    \cventry{}{University of Texas at Austin and Sandia National Laboratories}{Rising Stars in Computational and Data Sciences}{\textnormal{\textit{April 2019}}}{}{}
\awardspace
    \cventry{}{Association for Women in Science, Notre Dame Chapter}{Outstanding Member Award}{\textnormal{\textit{May 2017 \& 2018}}}{}{}
\awardspace
    \cventry{}{Survey Research Methods, Government Statistics, and Social Statistics Sections | \$800}{Joint Statistical Meetings Student Paper Award}{\textnormal{\textit{Jan. 2017}}}{}{}
\awardspace
    \cventry{}{American Statistical Association and Caucus for Women in Statistics | \$1,000}{Gertrude M. Cox Scholarship}{\textnormal{\textit{July 2016}}}{}{}
\awardspace
    \cventry{}{University of Notre Dame - Graduate Student Union | \$300}{1st Place Poster Presentation - Late Stage Researcher - College of Science Division}{\textnormal{\textit{April 2016}}}{}{}
\awardspace
    \cventry{}{University of Notre Dame - Graduate School | \$1,000}{3 Minute Thesis People's Choice Award}{\textnormal{\textit{March 2016}}}{}{}
\awardspace
    \cventry{}{ISU College of Science and Engineering}{Best and Brightest Distinguished Student Award}{\textnormal{\textit{May 2013}}}{}{}
\awardspace
    \cventry{}{ISU Cultural Diversity}{Outstanding Academic Excellence}{\textnormal{\textit{May 2013}}}{}{}
\awardspace
    \cventry{}{Society of Physics Students (SPS) National Organization | \$3,500}{Sigma Pi Sigma Outstanding Leadership Award}{\textnormal{\textit{June 2011}}}{}{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Travel Awards
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-10pt}
\section{Travel Awards}

    \cventry{}{Institute of Mathematical Statistics \& National Science Foundation | \$800}{New Researcher Conference Travel Award}{\textnormal{\textit{July 2019}}}{}{}
\awardspace
    \cventry{}{American Statistical Association | \$600}{Spring Research Conference Conference Travel Award}{\textnormal{\textit{May 2019}}}{}{}
\awardspace
    \cventry{}{National Science Foundation \& Google | \$700}{Women in Statistics and Data Science Conference Travel Award}{\textnormal{\textit{Aug. 2017}}}{}{}
\awardspace
    \cventry{}{Anita Borg Institute \& National Institute of Standards and Technology | All Expenses Covered}{Grace Hopper Celebration of Women in Computing Student Scholarship }{\textnormal{\textit{May 2017}}}{}{}
\awardspace
    \cventry{}{Graduate Student Union at Notre Dame | \$250}{Graduate Student Union Conference Presentation Travel Award}{\textnormal{\textit{April 2017}}}{}{}
\awardspace
    \cventry{}{ACMS | \$500}{ACMS Graduate Professional Development Travel Award}{\textnormal{\textit{Jan. 2017}}}{}{}
\awardspace  
    \cventry{}{R Studio | All Expenses Covered}{R Studio Conference Diversity Travel Award}{\textnormal{\textit{Jan. 2017}}}{}{}
\awardspace
    \cventry{}{National Science Foundation, Statistical Computing \& Graphics, and Google | \$500}{Women in Statistics and Data Science Conference Travel Award}{\textnormal{\textit{Aug. 2016}}}{}{}

% \newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Publications
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Publications}

\noindent\underline{\textbf{Books}}

\begin{etaremune}[topsep=0pt, itemsep=6pt, partopsep=0pt, parsep=0pt]
  \item \textbf{Bowen, CMK.} ``Protecting Your Privacy in a Data-Driven World.'' (Nov. 2021) \textit{Routledge-CRC Press}, American Statistical Association-CRC Series on Statistical Reasoning in Science and Society.
\end{etaremune}

\vspace{6pt}
\noindent\underline{\textbf{Refereed Publications}}
\vspace{4pt}
\begin{etaremune}[topsep=0pt, itemsep=3pt, partopsep=0pt, parsep=0pt]
    \item \textbf{Bowen, CMK.}, Bryant, V., Burman, L., Khitatrakun, S., McClelland, R., Mucciolo, L., Pickens, M., and Williams, A. (2022) ``Synthetic Individual Income Tax Data: Promises and Challenges.'' to appear in  \textit{National Tax Journal}.
    
    \item \textbf{Bowen, CMK.}, Bryant, V., Burman, L., Czajka, J., Khitatrakun, S., MacDonald, G., McClelland, R., Mucciolo, L., Pickens, M., Ueyama, K., Williams, A., Wissoker, D., and Zwiefel, N. (2022) ``Synthetic Individual Income Tax Data: Methodology, Utility, and Privacy Implications.'' to appear in  \textit{International Conference on Privacy in Statistical Databases}.
    
    \item Liu, F., Eugenio, E., Jin, I., and \textbf{Bowen, CMK}. (2022) ``Differentially Private Synthesis and Sharing of Network Data via Bayesian Exponential Random Graph Models.'' \textit{Journal of Survey Statistics and Methodology}, 10(3), 753-784.\\
    doi: 10.1093/jssam/smac017
    
    \item Garfinkel, S. and \textbf{Bowen, CMK} (2022) ``Preserving Privacy While Sharing Data.'' \textit{MIT Sloan Management Review}, 63 (3), 1-4.
    
    \item \textbf{Bowen, CMK} and Garfinkel, S. (2021) ``The Philosophy of Differential Privacy.'' \textit{Notices of the American Mathematical Society}, 68(10), pages 1727-1739.\\
    doi: 10.1090/noti2363
    
    \item \textbf{Bowen, CMK.}, Liu, F., Su, B. (2021) ``Differentially Private Data Release via Statistical Election to Partition Sequentially.'' \textit{METRON}, Issue 79, pages 1-31.\\
    doi: 10.1007/s40300-021-00201-0
    
    \item \textbf{Bowen, CMK.} and Snoke, J. (2021) ``Comparative Study of Differentially Private Synthetic Data Algorithms from the NIST PSCR Differential Privacy Synthetic Data Challenge.'' \textit{Journal of Privacy and Confidentiality}, 11(1).\\
    doi: 10.29012/jpc.748
    
    \item Snoke, J., and \textbf{Bowen, CMK.} (2020) ``How Statisticians Should Grapple with Privacy in a Changing Data Landscape.'' \textit{CHANCE}, 33(4), pages 6-13.\\
    doi: 10.1080/09332480.2020.1847947
    
    \item \textbf{Bowen, CMK.}, Bryant, V., Burman, L., Khitatrakun, S., McClelland, R., Stallworth, P., Ueyama, K., Williams, A. (2020) ``A Synthetic Supplemental Public Use File of Low-Income Information Return Data: Methodology, Utility, and Privacy Implications.'' \textit{International Conference on Privacy in Statistical Databases}, pages 257-270. Springer, Cham.
    
    \item Liu, F., Eugenio, E., Jin, I., and \textbf{Bowen, CMK}. (2020) ``Differentially Private Generation of Social Networks via Exponential Random Graph Models.'' \textit{Proceedings of 2020 IEEE 44th Annual Computers, Software, and Applications Conference (COMPSAC)}, pages 1695-1700.\\
    doi: 10.1109/COMPSAC48688.2020

    \item \textbf{Bowen, CMK.} and Liu, F. (2020) ``Comparative Study of Differentially Private Data Synthesis Methods.'' \textit{Statistical Science}, 35(2), pages 280-307.

    \item \textbf{Bowen, CMK.}, DeBardeleben, N., Blanchard, S., Anderson-Cook, C. (2019) ``Do Solar Proton Events Reduce the Number of Faults in Supercomputers?: A Comparative Analysis of Faults during and without Solar Proton Events." \textit{2019 IEEE International Reliability Physics Symposium}.

    \item \textbf{Bowen, CMK.} and Eugenio, E. (2017) ``Where's Wenda:  An Activity on Teaching Middle School Students Data Privacy.'' \textit{Statistics Teacher}, Issue No. 1.
    
    \item Myers, K., Lawrence, E., Fugate, M., \textbf{Bowen, CMK.}, Ticknor, L., Woodring, J., Wendelberger, J., Ahrens, J. (2016) ``Partitioning a Large Simulation as It Runs.'' \textit{Technometrics}, 58(3), pages 329-340. \\
    doi: 10.1080/00401706.2016.1158740

    \item \textbf{Bowen, CMK.}, Liu, F., \& Wheeler, J. (2015) ``Are More of My Patients Developing Side Effects than Expected.'' \textit{Practical Radiation Oncology},5(3), pages e255-e261.\\
    doi: 10.1016/j.prro.2014.10.007
\end{etaremune}

\vspace{4pt}
% \newpage
\noindent\underline{\textbf{Under Review/Preprint}}
\begin{etaremune}[topsep=0pt, itemsep=4pt, partopsep=0pt, parsep=0pt]
    \item Williams, A. R., Snoke, J., \textbf{Bowen, CMK}., and Barrientos, A. F. (2022) ``Disclosing Economists' Privacy Perspectives: A Survey of American Economic Association Members on Differential Privacy and Data Fitness for Use Standards.''
    
    \item Barrientos, A. F., Williams, A. R., Snoke, J., and \textbf{Bowen, CMK}. (2021) ``A Feasibility Study of Differentially Private Summary Statistics and Regression Analyses for Administrative Tax Data.'' arXiv:2110.12055
\end{etaremune}

% \newpage
\vspace{4pt}
\noindent\underline{\textbf{Research Reports (Non-Refereed)}}
\vspace{4pt}
\begin{etaremune}[topsep=0pt, itemsep=3pt, partopsep=0pt, parsep=0pt]
    \item Morrison, G., and \textbf{Bowen, CMK}. (2022) ``Internet First or Internet Choice? Identifying Factors to Predict Low Self-Response Rates on the 2020 Census.'' \textit{Urban Institute}.
    
    \item Barrientos, A. F., Williams, A. R., Snoke, J., and \textbf{Bowen, CMK}. (2021) ``Differentially Private Methods for Validation Servers: A Feasibility Study of Differentially Private Summary Statistics and Regression Analyses for Administrative Tax Data.'' \textit{Urban Institute}.
    
    \item Taylor, S., MacDonald, G., Ueyama, K., and \textbf{Bowen, CMK.} (2021) ``A Privacy-Preserving Validation Server Prototype.'' \textit{Urban Institute}.
        
    \item \textbf{Bowen, CMK.} (2021) ``Personal Privacy and the Public Good: Balancing Data Privacy and Data Utility.'' \textit{Urban Institute}.
    
    \item \textbf{Bowen, CMK.}, Narayanan, A., Scally, C. (2021) ``Using Differential Privacy to Advance Rural Economic Development: Applying Data Privacy and Confidentiality Methods to Industry Employment Data.'' \textit{Urban Institute}.
    
    \item \textbf{Bowen, CMK.}, Burman, L., Khitatrakun, S., MacDonald, G., McClelland, R., Stallworth, P., Ueyama, K., Williams, A., Zwiefel, N. (2020) ``A Synthetic Supplemental Public-Use File of Low-Income Information Return Data: Methodology, Utility, and Privacy Implications.'' \textit{Urban Institute}
    
    \item \textbf{Bowen, CMK.} (2016) ``NSF GRIP Report: American Community Survey Simulation Study." \textit{U.S. Census Bureau}.  
\end{etaremune}

\vspace{6pt}
\noindent\underline{\textbf{Blogs and Professional Service Publications}}
\vspace{4pt}
\begin{etaremune}[topsep=0pt, itemsep=4pt, partopsep=0pt, parsep=0pt]
    % \item Messner, M. and \textbf{Bowen, CMK.} (2022) ``Spotlight on the Government Statistics Section of the American Statistical Association.'' \textit{CHANCE}, 35(3), pages 4-8.
    
    \item Hu, J. and \textbf{Bowen, CMK.} (2022) ``Prescribing Privacy: Human and Computational Resource Limitations and What Statisticians and Data Scientists Can Do.'' \textit{Amstat News}, September Issue.
    
    \item \textbf{Bowen, CMK.} (2022) ``SDSS 2022: Connecting and Influencing Our Society.'' \textit{Amstat News}, August Issue.
    
    \item Schwabish, J. and \textbf{Bowen, CMK.} (2022) ``Data4Kids: A Collaborative Project to Teach Kids about Data.'' \textit{Nightingale}.
    
    \item \textbf{Bowen, CMK.} and Schwabish, J. (2022) ``How Data4Kids Helps Students Log on to Learn.'' \textit{Data@Urban}.

    \item \textbf{Bowen, CMK.} (2022) ``Beyond Big Data: Supporting Students and Early-Career Professionals.'' \textit{Amstat News}, February Issue.
    
    \item \textbf{Bowen, CMK.} (2022) ``The Art of Data Privacy.'' \textit{Significance Magazine}, February Issue.
    
    \item \textbf{Bowen, CMK.} (2021) ``Analyzing the Quality of 2020 Census: Understanding the US Population Puzzle.'' \textit{Data@Urban}.

    \item \textbf{Bowen, CMK.} (2021) ``Claire McKay Bowen Talks Data Privacy.'' \textit{Amstat News}, December Issue.
    
    \item \textbf{Bowen, CMK.} (2021) ``Utility Metrics for Differential Privacy: No One-Size-Fits-All.'' \textit{Differential Privacy: NIST Blog Series}.
    
    \item \textbf{Bowen, CMK.} (2021) ``Data Science and Statistics Influencing Science, Technology, and Society.'' \textit{Amstat News}, October Issue.
    
    \item \textbf{Bowen, CMK.} (2021) ``Sailing Your Own Path: An Interview with Jeri Mulrow.'' \textit{Amstat News}, September Issue.

    \item \textbf{Bowen, CMK.} (2021) ``Star Statisticians Offer Career Advancement Advice.'' \textit{Amstat News}, September Issue.    
    
    \item Martinez, W., \textbf{Bowen, CMK.}, LaLonde, D. (2021) ``Beyond Big Data: Shaping the Future - SDSS 2021.'' \textit{Amstat News}, August Issue.   
    
    \item \textbf{Bowen, CMK.} and Mannshardt, E. (2021) ``Committee on Career Development Announces Initiative Lineup.'' \textit{Amstat News}, June Issue.

    \item \textbf{Bowen, CMK.} (2021) ``How data privacy methods can hide the real data story.'' \textit{International Statistical Institute}, Statisticians React to the News.
    
    \item \textbf{Bowen, CMK.}, Williams, A., and Narayanan, A. (2021) ``To Advance Racial Equity, Releasing Disaggregated Data while Protecting Privacy Will Be Key.'' \textit{Urban Wire}. 
    
    \item Brown, S, MacDonald, G., and \textbf{Bowen, CMK.} (2021) ``How the Federal Government Can Use Data to Make the Most of the Executive Order on Racial Equity.'' \textit{Urban Wire}. 

    \item \textbf{Bowen, CMK.} (2020) ``To bike or not to bike...in a group?'' \textit{International Statistical Institute}, Statisticians React to the News.

    \item \textbf{Bowen, CMK.} (2020) ``My ASA Story.'' \textit{Amstat News}, December Issue.

    \item Chase, E., \textbf{Bowen, CMK.}, Director, H., Baladandayuthapani, V. and Pierson, S. (2020) ``Panel Shares Advice on Applying for NSF Fellowships.'' \textit{Amstat News}, November Issue.

    \item \textbf{Bowen, CMK.} and Mannshardt, E. (2020) ``Committee on Career Development Holds Virtual Office Hours with Experts.'' \textit{STAT tr@k News}, June Issue.

    \item \textbf{Bowen, CMK.} and Mannshardt, E. (2020) ``Reaching Your Networking Peak: A Guided Networking Session at JSM.'' \textit{Amstat News}, April Issue.
    
    \item \textbf{Bowen, CMK.} (2020) ``Will the Census Bureau's data privacy efforts erase rural America?'' \textit{Urban Wire}. 
    
    \item Snoke, J. and \textbf{Bowen, CMK.} (2019) ``Differential Privacy: What Is It?'' \textit{Amstat News}, March Issue.
\end{etaremune}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Media
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Media}
\begin{etaremune}[topsep=0pt, itemsep=2pt, partopsep=0pt, parsep=0pt]
    \item May 2022. \textit{The Data Privacy Scientist, Claire McKay Bowen}. Radiations.
    
    \item April 2022. \textit{Dr. Claire McKay Bowen}. The PolicyViz Podcast.
    
    \item April 2022. \textit{Ruobin Gong interviews Claire McKay Bowen}. Institute of Mathematical Statistics Bulletin.
    
    \item Feb. 2022. \textit{Can Third Graders Learn Data Science? These Researchers Say Yes}. EdSurge.
    
    \item Jan. 2022. \textit{ISU graduate writes book on data privacy}. Local News 8 in Idaho.
    
    \item Jan. 2022. \textit{Idaho State Alumna Authors Book on Data Privacy}. Idaho State University News.

    \item Aug. 2021. \textit{The Life of an ASA Conference Program Chair}. Practical Significance.    

    \item June 2021. \textit{Career Story}. Significance.
    
    \item May 2021. \textit{2021 COPSS Award Winners}. Amstat News.
    
    \item April 2021. \textit{People of Science Feature}. Science is US.
    
    \item April 2021. \textit{The Data Privacy Landscape is Changing}. Stats + Stories Podcast.
    
    \item Feb 2021. \textit{Privacy Talk with Claire McKay Bowen}. Privacy Talk Interview.

    \item March 2020. \textit{Celebrating Women in Statistics}. Women's History Month feature in Amstat News.

    \item March 2020. \textit{Data\@Urban Digital Discussions ft. Graham MacDonald and Claire Bowen}. Data\@Urban Digital Discussions, webinar hosted by the Urban Institute.
    
    \item Nov. 2019. \textit{Differential Privacy? w/ Dr. Claire McKay Bowen}. Data Science Imposters Podcast.
\end{etaremune}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Presentations
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \newpage
\section{Invited Presentations}

\underline{\textbf{\large Scientific Meetings}}\normalsize
\vspace{6pt}
\begin{etaremune}[topsep=0pt, itemsep=2pt, partopsep=0pt, parsep=0pt]
    
    \item Aug. 2022. \textit{The Art of Data Privacy}. IQT Tech Focus Day, Washington D.C.
    
    \item July 2022. \textit{Comparative Study of Differentially Private Data Synthesis Methods}. International Society for Bayesian Analysis World Meeting, Bonaventure, Montreal, Quebec, Canada.
    
    \item June 2022. \textit{Safely Expanding Research Access to Administrative Tax Data}. SPOKES Privacy Technology Conference, Virtual.
    
    \item April 2022. \textit{A Feasibility Study of Differentially Private Summary Statistics and Regression Analyses for Administrative Tax Data}. Noisy Measurements Research Workshop, Rutgers University at New Brunswick, NJ.
    
    \item April 2022. \textit{Advancing Data Privacy-Preserving Methodologies}. Joint Mathematics Meetings, Virtual. \textbf{Session organizer and presenter.}

    \item Feb. 2022. \textit{Personal Privacy and the Public Good}. Association for the Advancement of Artificial Intelligence Workshop of Privacy Preserving Artificial Intelligence.
    
    \item Sept. 2021. \textit{Generating Synthetic Data for Data Privacy in R}. noRth R, Virtual.

    \item Aug. 2021. \textit{Another Invisible Threat: Unequal Privacy Cost of Tracing COVID-19}. Joint Statistical Meetings, Virtual.
    
    \item July 2021. \textit{Differential Privacy in the Real-World}. American Association for Public Opinion Research Webinar.

    \item June 2020. \textit{Telling a Visual Story in Big Data: Case Studies on Interactive Visualizations for Supercomputer Data}. Symposium on Data Science and Statistics, Virtual.
  
    \item June 2020. \textit{Best Practices for Leading Data Science Efforts in Your Organization}. Symposium on Data Science and Statistics, Virtual.
  
    \item April 2020. \textit{Differential Privacy: What is it?} Women in Data Science Conference, the Virginia Tech at Blacksburg, VA, Virtual.

    \item Aug. 2016. \textit{Differentially Private Data Synthesis Partitioning for Big Data}. Joint Statistical Meetings, McCormick Place at Chicago, IL.
    
    \item Sept. 2015. \textit{Differential Privacy \& the Mosaic Effect}. NSF-National Center for Science and Engineering Statistics Expert Panel on Confidentiality Protection, SRI at Arlington, VA.

\vspace{6pt}
\hspace{-0.30in}\underline{\textbf{\large Seminars}}\normalsize
    \item Aug. 2022. \textit{Dr. Claire McKay Bowen: From Physics to Public Policy}. Webinar hosted by Technically Private.
    
    \item Aug. 2022. \textit{Protecting Your Privacy in a Data-Driven World}. Webinar hosted by DC AAPOR, Virtual.
    
    \item May 2022. \textit{Protecting Your Privacy in a Data-Driven World}. Epidemiology and Biostatistics Seminar Series, Drexel University at Philadelphia, PA.
    
    \item May 2022. \textit{Data4Kids: Virtually Teaching Kids about Data Science}. Cyberinfrastructure for Network Science Center Research Showcase, Indiana University, Virtual.
    
    \item March 2022. \textit{Protecting Your Privacy in a Data-Driven World}. Webinar hosted by Abt. Associates, Virtual.
    
    \item March 2022. \textit{Safely Expanding Research Access to Administrative Tax Data}. Neyman Seminar Series, University of California Berkeley, Virtual.
    
    \item March 2022. \textit{Protecting Your Privacy in a Data-Driven World}. McDonough School of Business at Georgetown University, Virtual.
    
    \item March 2022. \textit{Dr. Claire McKay Bowen: From Physics to Public Policy}. Journeys in Statistics and Data Science, Penn State University, Virtual.
        
    \item Feb. 2022. \textit{Data Privacy Preserving Applications with R}. Webinar hosted by R-Ladies Baltimore.

    \item Jan. 2022. \textit{Protecting Your Privacy in a Data-Driven World}. Webinar hosted by the Washington Statistical Society, Virtual.
    
    \item Dec. 2021. \textit{Statistics and Data Science at the Urban Institute}. Statistics Seminar at Florida State University, Virtual.
    
    \item Nov. 2021. \textit{Protecting Your Privacy in a Data-Driven World}. Biostatistics Seminar Series, Johns Hopkins University at Baltimore, MD.
    
    \item Sept. 2021. \textit{Protecting Your Privacy in a Data-Driven World}. Statistics Seminar Series, Virginia Tech at Blacksburg, VA. \textcolor{blue}{My 100th Talk}
    
    \item April 2021. \textit{How the Federal Government Can Use Data to Make the Most of the Executive Order on Racial Equity}. Heinz College at Carnegie Mellon University, Virtual.

    \item Feb. 2021. \textit{How Statistics Protects Your Privacy in a World Driven by Data}. STEM Seminar Series, Henderson State University, Virtual.

    \item Nov. 2020. \textit{Data Privacy in the Real World}. Statistics Seminar Series, Bureau of Labor Statistics, Virtual.

    \item Sept. 2020. \textit{Data Privacy in the Real World}. Statistics Seminar Series, University of Pittsburgh, Virtual.
        
    \item Aug. 2020. \textit{Data Privacy in the Real World with Claire McKay Bowen, PhD}. Webinar hosted by DataBasement, SWFL Coders, SWFL PyLadies, Miami PyLadies, and SWFL Data MeetUp.
    
    \item Feb. 2020. \textit{Comparative Study of Differentially Private Synthetic Data Algorithms and Evaluation Standards}. Statistics Colloquia, University of California-Riverside at Riverside, CA.
    
    \item Feb. 2020. \textit{How to Tell a Less Flawed Data Story: Data Analytics, Data Communication, and Data Privacy}. Statistics Seminar, Bryant University at Provenance, RD.
    
    \item Sept. 2019. \textit{Comparative Study of Differentially Private Data Synthesis Methods}. Urban Institute at Washington, D.C.
    
    \item Oct. 2018. \textit{What is Data Science?} Data Science: Overview, Insights, and Path Forward Workshop, University of Texas-El Paso at El Paso, TX.
    
    \item Dec. 2017. \textit{Statistical Tests to Elect Partitions Sequentially (STEPS) and Its Applications in Differentially Private Release and Analysis of Voter Registration Data}. Applied Statistics Group, Lawrence Livermore National Laboratory at Livermore, CA.
    
    \item Oct. 2017. \textit{Statistical Allocation for Epsilon: A Differentially Private Application and Evaluation on Voter Registration Data}. Applied and Computational Statistics Group, National Institute of Standards and Technology at Boulder, CO.
    
    \item Sept. 2017. \textit{Statistical Allocation for Epsilon: A Differentially Private Application and Evaluation on Voter Registration Data}. Statistical Sciences Group, Sandia National Labs at Albuquerque, NM.
    
    \item Sept. 2017. \textit{Statistical Allocation for Epsilon: A Differentially Private Application and Evaluation on Voter Registration Data}. Applied Statistics and Computational Modeling Group, Pacific Northwest National Laboratory at Richland, WA.
    
    \item April 2017. \textit{Comparative Study of Differentially Private Data Synthesis Methods}. Department of Mathematics and Statistics, University of Maryland - Baltimore County at Baltimore, MD.
    
% \newpage
\vspace{6pt}
\hspace{-0.30in}\underline{\textbf{\large Moderated Panels}}\normalsize
    \item June 2022. \textit{Science and Technology Policy Panel}. Symposium on Data Science and Statistics, Pittsburgh, PA.
    
    \item Feb. 2022. \textit{Urban Institute Equity Dialogue with Fanta Traore}. Webinar hosted by the Urban Institute.
    
    \item June 2021. \textit{2020 Census}. Symposium on Data Science and Statistics, Virtual.
    
    \vspace{6pt}
% \newpage
\hspace{-0.30in}\underline{\textbf{\large Panels}}\normalsize
    \item April 2022. \textit{Writing and communicating well}. Rising Stars in Computational and Data Sciences Workshop.

    \item Feb. 2022. \textit{Differential Privacy and disparate impacts in downstream decisions and learning tasks}. Association for the Advancement of Artificial Intelligence Workshop of Privacy Preserving Artificial Intelligence.
    
    \item Nov. 2021. \textit{Panel Discussion About Careers in Industry and Government}. Electronic Undergraduate Statistics Research Conference, Virtual.

    \item May 2021. \textit{Career Advice Panel}. Department of Statistics, North Carolina State University, Virtual.
    
    \item April 2021. \textit{Think Tanks Panel}. Graduate Student Union Professional Development Series, University of Notre Dame, Virtual.
    
    \item April 2021. \textit{Judges Panel: The soft skills of data analytics}. DataFest, Bryant University, Virtual.
\end{etaremune}

% \newpage
%%%%%%% Contributed
\vspace{-10pt}
\section{Contributed Presentations}
\underline{\textbf{\large Funder/Stakeholder Presentations}}\normalsize
\vspace{4pt}
\begin{etaremune}[topsep=0pt, itemsep=0.75pt, partopsep=0pt, parsep=0pt]
    \item July 2022. \textit{Data Privacy and Public Policy at the Urban Institute.} FTAC Adoption Subgroup.
    
    \item May 2022. \textit{Safely Expanding Access to Administrative Tax Data for Better Public Policymaking.} Urban Institute's Board of Trustees.
    
    \item April 2022. \textit{Privacy threats and re-identification risks.} Advisory Committee on Data for Evidence Building Technical Infrastructure Subcommittee Meeting.
    
    \item March 2022. \textit{Data4Kids: Virtually Teaching Kids about Data Science.} South Big Data Hub S.E.E.D.S. Panel for the Funders and Grant Recipients.
    
    \item Oct. 2021. \textit{Synthetic Public Use File (SynPUF) and Future Work.} Administrative Tax Data Project for the Advisory Board, Funders, and Guests.
    
    \item July 2021. \textit{Validation Server Project: Advisory Board Meeting.} Validation Server Project for the Advisory Board, Funders, and Guests.
    
    \item July 2021. \textit{Expanding Access to Confidential Administrative Tax Data with Synthetic Data and Validation Server.} Sloan Foundation, Actuate, Georgetown University, the University of Illinois at Urbana-Champaign, and the Urban Institute
    
    \item April 2021. \textit{Creating a Synthetic Public Use File.} Administrative Tax Data Project for the Internal Revenue Service Statistics of Income Division.

    \item Dec. 2020. \textit{Using Differential Privacy to Advance Rural Economic Development: Applying Data Privacy and Confidentiality Methods to Industry Employment Data.} Fleishman Award Project for the Bureau of Labor Statistics.
    
    \item Dec. 2020. \textit{Validation Server Project: Advisory Board Meeting.} Validation Server Project for the Advisory Board, Funders, and Guests.
    
    \item Sept. 2020. \textit{Validation Server Project - Kickoff Meeting.} Validation Server Project for the Internal Revenue Service Statistics of Income Division and National Science Foundation.
    
    \item July 2020. \textit{Creating a Synthetic Public Use File of Nonfilers.} Administrative Tax Data Project for the Advisory Board, Funders, and Guests.
    
    \item Oct. 2019. \textit{Functional Data Analysis for Iterative Design.} Laboratory Directed Research \& Development Project for the Review Committee and Guests.

\vspace{6pt}
% \newpage
\hspace{-0.30in}\underline{\textbf{\large Panels}}\normalsize
    \item Aug. 2022. \textit{Virtual Lunch: A Conversation with Urban Authors}. Urban Institute, Virtual.
    
    \item Oct. 2021. \textit{Wrapping Up and Moving On: Advice for the Final Stretch of Graduate School}. Women in Statistics and Data Science Conference, Virtual.
    
    \item Oct. 2021. \textit{Which Path Should I Choose? A Discussion of Employment in Academia, Industry, Government, and Nonprofits}. Women in Statistics and Data Science Conference, Virtual.
    
    \item Oct. 2020. \textit{Data Governance in the Era of Big Data}. Women in Statistics and Data Science Conference, Virtual.
    
    \item April 2020. \textit{Postdoc Positions}. Virtual Office Hours, webinar hosted by the American Statistical Association Committee on Career Development. \textbf{Moderator}
    
    \item Oct. 2018. \textit{Implicit Bias and Power Dynamics: How We Can Change the Culture}. Women in Statistics and Data Science Conference at Cincinnati, OH.

    \item March 2015. \textit{Graduate School Advice Panel}.  Regional Society of Women Engineers Conference at Notre Dame, IN.
    
    \item Sept. 2014. \textit{Graduate School Advice Panel}.  University of Notre Dame Career Center at Notre Dame, IN.
    
% \newpage
\vspace{6pt}
\hspace{-0.30in}\underline{\textbf{\large Oral Presentations}}\normalsize
    \item Sept. 2022. \textit{Synthetic Individual Income Tax Data: Methodology, Utility, and Privacy Implications}. International Conference on Privacy in Statistical Databases at Paris, France. \textbf{Will be presenting.}
    
    \item April 2022. \textit{Protecting Your Privacy in a Data-Driven World}. Statistical Methods Group Brown Bag at the Urban Institute.
    
    \item Feb. 2022. \textit{Urban Formatting in LaTeX.} Urban Seed Fund Symposium at the Urban Institute.

    \item Nov. 2021. \textit{Data Science and Public Policy}. ASA Student Chapter, University of Georgia ASA Student Chapter Seminar, Virtual.
    
    \item Nov. 2021. \textit{Synthetic Public Use File of Administrative Tax Data: Methodology, Utility, and Privacy Implications}. Federal Committee on Statistical Methodology Conference, Virtual.
    
    \item Sept. 2021. \textit{Validation Server Project: SmartNoise Use Case}. OpenDP Community Meeting, Virtual.
    
    \item Sept. 2021. \textit{Networking Prep: How to Network in a Virtual Landscape}. StatFest 2021, Virtual.
    
    \item Nov. 2020. \textit{Discussion on ``Disclosure Control Practices on BLS Administrative Data''}. Annual Conference on Taxation, Virtual. \textbf{Session organizer and presenter.}
    
    \item Oct. 2020. \textit{Another Invisible Threat: Unequal Privacy Cost of Tracing COVID-19}. Grace Hopper Celebration, Virtual.
    
    \item Sept. 2020. \textit{NSF Graduate and Postdoctoral Fellowships: Opportunities and Advice}. Webinar hosted by ASA Committee on Funded Research.
    
    \item Sept. 2020. \textit{IRS Validation Server Initiative}. Webinar hosted by Internal Revenue Service Statistics of Income Division.
    
    \item Aug. 2020. \textit{Data Challenges: Innovating Diverse Solutions}. Joint Statistical Meetings, Virtual. \textbf{Session organizer and presenter.}
    
    \item July 2020. \textit{Setting Policymaking Priorities on Differential Privacy}. Association of Public Data Users Annual Conference, Virtual.
    
    \item June 2020. \textit{Differential Privacy: What is it?} SIAM Conference on Mathematics of Data Science, Virtual. \textbf{Session organizer and presenter}
    
    \item May 2020. \textit{Data\@Urban Digital Discussions Teaching Data to Kids}. Data\@Urban Digital Discussions, webinar hosted by the Urban Institute.
    
    \item April 2020. \textit{Meet a Statistician: Claire Bowen}. Meet a Statistician Series, webinar hosted by This is Statistics.
    
    \item April 2020. \textit{Optimizing Data to Advance Rural Economic Development}. Fleishman Innovation Award Presentation at the Urban Institute.
    
    \item March 2020. \textit{Social Media}. Caucus for Women in Statistics Lunch and Learn, webinar hosted by the Caucus for Women in Statistics.
    
    \item July 2019. \textit{Iterative Design with Humans-in-the-Loop for Functional Data Analysis}. Joint Statistical Meetings at Denver, CO. 
    
    \item July 2019. \textit{How to Get that Funding: Writing Successful Scholarship Applications}. Los Alamos National Laboratory at Los Alamos, NM.
    
    \item June 2019. \textit{Telling a Visual Story in Big Data}. Science in 3, Los Alamos National Laboratory at Los Alamos, NM. 
    
    \item April 2019. \textit{Telling a Visual Story in Big Data: Case Studies on Interactive Visualizations for Supercomputer Data}. Rising Stars in Computational and Data Sciences Workshop at the University of Texas-Austin in Austin, TX.
    
    \item April 2019. \textit{Do Solar Proton Events Reduce the Number of Faults in Supercomputers?: A Comparative Analysis of Faults during and without Solar Proton Events}. IEEE International Reliability Physics Symposium at Monterrey, California.
    
    \item Sept. 2018. \textit{How to Get that Funding: Writing Successful Scholarship Applications}. Grace Hopper Celebration at Houston, TX.
    
    \item Oct. 2018. \textit{How to Get that Funding: Writing Successful Scholarship Applications}. Women in Statistics and Data Science Conference at Cincinnati, OH.
    
    \item Aug. 2018. \textit{Statistical Tests to Elect Partitions Sequentially (STEPS) and Its Applications in Differentially Private Release and Analysis of Voter Registration Data}. Joint Statistical Meetings at Vancouver, BC in Canada.
    
    \item July 2018. \textit{Creating Your Own Luck at JSM}. Joint Statistical Meetings at Vancouver, BC in Canada.
    
    \item July 2018. \textit{Creating Your Own Luck}. Los Alamos National Laboratory at Los Alamos, NM.
    
    \item July 2018. \textit{How to Get that Funding}. Los Alamos National Laboratory at Los Alamos, NM.
    
    \item February 2018. \textit{Creating Your Own Luck}. University of Notre Dame at Notre Dame, IN.
    
    \item Nov. 2017. \textit{Statistical Tests to Elect Partitions Sequentially (STEPS) and Its Applications in Differentially Private Release and Analysis of Voter Registration Data}. Statistics Seminar Series University of Notre Dame at Notre Dame, IN.
    
    \item Aug. 2017. \textit{Comparative Study of Differentially Private Data Synthesis Methods}. Joint Summer Meeting University of Notre Dame at Notre Dame, IN.
    
    \item Aug. 2017. \textit{Comparative Study of Differentially Private Data Synthesis Methods}. Joint Statistical Meetings at Baltimore, MD.\\
    \textcolor{blue}{2017 JSM Student Paper Award}
    
    \item April 2017. \textit{Comparative Study of Differentially Private Data Synthesis Methods}. Society for Industrial and Applied Mathematics Student Seminar, University of Notre Dame at Notre Dame, IN.
    
    \item May 2017. \textit{Statistical Allocation for Epsilon: A Differentially Private Application and Evaluation on Voter Registration Data}. College of Science - Joint Annual Meeting, University of Notre Dame at Notre Dame, IN.
    
    \item Oct. 2016. \textit{Differentially Private Data Synthesis Partitioning for Big Data}. Regional Women in Science Conference, University of Notre Dame at Notre Dame, IN. 
    
    \item Sept. 2016. \textit{What is Differential Privacy}. Center for Statistical Research Methodology Monthly Group Meeting, US Census Bureau at Suitland, MD. 
    
    \item July 2016. \textit{Differentially Private Data Synthesis Partitioning for Big Data}. Talking to Ourselves, Los Alamos National Laboratory at Los Alamos, NM.
    
    \item July 2016. \textit{Applying Scholarships, Fellowships, and Grants Seminar}. Los Alamos National Laboratory at Los Alamos, NM.
    
    \item March 2016. \textit{Big Brother in Big Data}. Three Minute Thesis Competition, University of Notre Dame at Notre Dame, IN.
    
    \item Sept. 2015. \textit{An In Situ Approach for Approximating Complex Computer Simulations and Identifying Important Time Steps}. New Technologies, New Knowledge - Center for Digital Scholarship Lightning Talks, University of Notre Dame at Notre Dame, IN.
    
    \item Aug. 2015. \textit{Data Privacy via Integration of Data Synthesis and Differential Privacy}. Joint Statistical Meeting, Washington Convention Center at Seattle, WA.
    
    \item July 2015. \textit{An In Situ Approach for Approximating Complex Computer Simulations and Identifying Important Time Steps}. 2015 Computing and Information Technology Student Mini Showcase, Los Alamos National Laboratory at Los Alamos, NM.
    
    \item July 2015. \textit{An In Situ Approach for Approximating Complex Computer Simulations and Identifying Important Time Steps}. T Division Lightning Talks, Los Alamos National Laboratory at Los Alamos, NM.
    
    \item July 2015. \textit{Applying Scholarships, Fellowships, and Grants Seminar}. Los Alamos National Laboratory at Los Alamos, NM.
    
    \item July 2015. \textit{An In Situ Approach for Approximating Complex Computer Simulations and Identifying Important Time Steps}. Talking to Ourselves, Los Alamos National Laboratory at Los Alamos, NM.
    
    \item June 2015. \textit{Data Privacy via Integration of Data Synthesis and Differential Privacy}. Talking to Ourselves, Los Alamos National Laboratory at Los Alamos, NM. 
    
    \item May 2014. \textit{Facilitated Morning Discussion}. Women in Statistics Conference at Cary, NC.
    
    \item March 2014. \textit{Are More of My Patients Experiencing Side Effects than Expected}. Association for Women in Science STEM Luncheon Series, University of Notre Dame at Notre Dame, IN.
    
    \item Dec. 2012. \textit{Differences between Experts and Novices in the Ability to Detect Changes in Images}. Honors Thesis, Idaho State University at Pocatello ID.
    
    \item April 2012. \textit{Investigating the Mechanisms of the Rho Helicase}. Idaho State University Undergraduate Research Symposium.
    
    \item April 2012. \textit{Investigating the Mechanisms of the Rho Helicase}. Society of Physics Zone 15 Meeting, Brigham Young University - Idaho at Rexburg, ID.
    
    \item March 2011. \textit{The Reflection and Transmission of Physical Optics and Waves in Physics Education Research}. Society of Physics Zone 15 Meeting, Utah State University at Logan, UT.\\
    \textcolor{blue}{Best Oral Presentation}
  
% \newpage
%%%%%%%% Poster
\vspace{8pt}
\hspace{-0.30in}\underline{\textbf{\large Poster Presentations}}\normalsize
    \item July 2019. \textit{Telling a Visual Story in Big Data: Case Studies on Interactive Visualizations for Supercomputer Data}. 21st Meeting of New Researchers in Statistics and Probability at Fort Collins, CO.
    
    \item May 2019. \textit{Telling a Visual Story in Big Data: Case Studies on Interactive Visualizations for Supercomputer Data}. Spring Research Conference, the Virginia Tech at Blacksburg, VA.
    
    \item April 2019. \textit{Telling a Visual Story in Big Data: Case Studies on Interactive Visualizations for Supercomputer Data}. Rising Stars in Computational and Data Sciences Workshop at the University of Texas-Austin in Austin, TX.
    
    \item June 2018. \textit{Noisy Edges and Traits Methods: Differentially Private Data Synthesis Methods for Social Network Data}. 2018 Joint Research Conference at Santa Fe, NM.
    
    \item Oct. 2017. \textit{Statistical Allocation for Epsilon: A Differentially Private Application and Evaluation on Voter Registration Data}. 2017 Women in Statistics and Data Science Conference at La Jolla, CA.
    
    \item Feb. 2017. \textit{Partitioning a Large Simulation as It Runs}. 2017 Women in Mathematics Symposium, Indiana University - Purdue University Indianapolis at Indianapolis, IN.
    
    \item Oct. 2016. \textit{Differentially Private Data Synthesis Partitioning for Big Data}. Women in Statistics and Data Science Conference, Crown Plaza Hotel at Charlotte Executive Park, NC. 
    
    \item April 2016. \textit{Partitioning a Large Simulation as It Runs}. 2016 Graduate Student Union Research Symposium, University of Notre Dame at Notre Dame, IN.\\
    \textcolor{blue}{1st Place - College of Science Division}
    
    \item July 2015. \textit{An In Situ Approach for Approximating Complex Computer Simulations and Identifying Important Time Steps}. 2015 Computing and Information Technology Student Mini Showcase, Los Alamos National Laboratory at Los Alamos, NM.
    
    \item Nov. 2012. \textit{Differences between Experts and Novices in the Ability to Detect Changes in Images}. Sigma Pi Sigma Quadrennial Meeting, Royal Caribbean Hotel at Orlando, FL.
    
    \item April 2012. \textit{Investigating the Mechanisms of the Rho Helicase}. Society of Physics Zone 15 Meeting, Brigham Young University - Idaho at Rexburg, ID.
    
    \item April 2012. \textit{Investigating the Mechanisms of the Rho Helicase}. Undergraduate Research Symposium, Idaho State University at Pocatello ID.
    
    \item April 2011. \textit{The Reflection and Transmission of Physical Optics and Waves in Physics Education Research}. Undergraduate Research Symposium, Idaho State University at Pocatello ID.
    
    \item March 2011. \textit{The Reflection and Transmission of Physical Optics and Waves in Physics Education Research}. Society of Physics Zone 15 Meeting, Utah State University at Logan, UT.
\end{etaremune}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Advising
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Student Advising and Mentoring}

\underline{\textbf{\large Research Advisees:}}\normalsize

    \begin{itemize}
        \item Morrison, Gabriel, \textit{Urban Institute}: research intern \hfill June 2021 - Dec. 2021
        \item Ortega, Spencer, \textit{LANL}: graduate research assistant \hfill June 2019 - Aug. 2019
        \item Tourangeau, Eva, \textit{LANL}: post bachelors research assistant \hfill July 2018 - 2019
        \item Quezada, Jazmin, \textit{LANL}: graduate research assistant \hfill June 2019
        \item Ahimbisibwe, Ashley, \textit{ND}: undergraduate research assistant \hfill Aug. 2017 - May 2018
    \end{itemize}

\vspace{6pt}
\underline{\textbf{\large Mentoring Programs:}}\normalsize

    \begin{itemize}
        \item Urban Institute \hfill 2021 \& 2022
        \item Smith College Data Science Program - Senior Project \hfill 2021
        \item Association for Public Policy Analysis \& Management \hfill 2020
    \end{itemize}

% \vspace{4pt}
% \cventry{}{}{NSF Graduate Research Fellowship Program (GRFP)}{\textnormal{\textit{}}}{}{
% \begin{itemize}
% \item Maintain and created one of the top NSF GRFP advice websites for potential applicants, helping indirectly hundreds of applicants every year.
% \item Advised sixteen NSF GRFP winners from six different fields and five universities.
% % \item The following list of students are winners of the NSF GRFP that directly benefited from my advice:
%     % \begin{itemize}
%     %     \item McCarthy, Orion Stefan, \textit{Uni. of Maryland College Park}: Geosciences - Marine Biology \hfill 2018
%     %     \item Rodriguez, Victor, \textit{Uni. of Michigan}: Engineering - Mechanical \hfill 2018
%     %     \item Flores, Jean Serrano, \textit{MIT}: Engineering - Mechanical \hfill 2017
%     %     \item DiPietro, Kelsey, \textit{ND}: Mathematical Sciences - Applied Mathematics \hfill 2016
%     %     \item Gonzales, Erica, \textit{ND}: Physics and Astronomy - Astronomy and Astrophysics \hfill 2016
%     %     \item Fields, Francisco, \textit{ND}: Life Sciences - Microbial Biology \hfill 2016
%     %     \item Forrest Fruscalzo, Heather, \textit{ND}: Life Sciences - other (specify) - Entomology \hfill 2016
%     %     \item Marshall, Jermaine, \textit{ND}: Comp/IS/Eng - other (specify) - Social Sensing \hfill 2016
%     %     \item Merson, Jacob, \textit{Rensselaer Polytechnic Institute}: Engineering - Mechanical\hfill 2016
%     %     \item Perlman, Michael, \textit{ND}: Mathematical Sciences - Algebra, Number Theory, and Combinatorics \hfill 2016
%     %     \item RichardWebster, Brandon, \textit{ND}: Comp/IS/Eng - Comp/IS/Eng - Robotics and Computer Vision \hfill 2016
%     %     \item Taylor, Angelique, \textit{ND}: Comp/IS/Eng - Computational Science and Engineering \hfill 2016
%     %     \item Chatwin, Warren, \textit{ND}: Life Sciences - Genomics \hfill 2015
%     %     \item Kalchik, Andrea, \textit{ND}: Psychology - Cognitive \hfill 2015
%     %     \item Marra, Amanda, \textit{ND}: Life Sciences - Developmental Biology \hfill 2015
%     %     \item Stephenson, Annie, \textit{Harvard}: Physics and Astronomy - Condense Matter Physics \hfill 2015
%     % \end{itemize}
% \end{itemize}}

% \newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Service
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Professional Activities and Affiliations}

% \vspace{6pt}
\underline{\textbf{\large National Professional Memberships:}}\normalsize
\begin{itemize}
    \item American Statistical Association \hfill Feb. 2014 - Present
    \item Caucus for Women in Statistics \hfill July 2016 - Present
    \item Institute of Mathematical Statistics \hfill Sept. 2019 - Present
    \item International Society for Bayesian Analysis \hfill Feb. 2022 - Present
\end{itemize}

\professionalspace
\underline{\textbf{\large Grant and Fellowship Proposal Review:}}\normalsize

\begin{itemize}
    \item Alfred P. Sloan \hfill 2021
    \item Grace Hopper Celebration Scholarship \hfill 2020
    \item National Science Foundation \hfill 2019, 2020, \& 2021
\end{itemize}

\professionalspace
\underline{\textbf{\large Editorial:}}\normalsize

\textbf{Editorial Board:}
\begin{itemize}
    \item Significance Magazine \hfill August 2022 - July 2025
\end{itemize}

\vspace{2pt}
\textbf{Guest Editor:}
\begin{itemize}
    \item Journal of Data Science \hfill June 2022 - June 2023
\end{itemize}

\vspace{2pt}
\textbf{Associate Editor:}
\begin{itemize}
    \item Technometrics \hfill Jan. 2022 - Dec. 2024
\end{itemize}

\vspace{4pt}
\textbf{Journal, Conference Proceeding, and Book Referee for:}
\vspace{-10pt}
\begin{multicols}{2}
    \begin{itemize}
        \item The American Statistician
        \item CRC Press
        \item ACM-IMS Foundations of Data Science
        \item IEEE Transactions on Information Forensics \& Security
        \item Journal of Privacy and Confidentiality
        \item Journal of Royal Statistical Society - Series A
        \item Journal of Statistical Theory and Practice
        \item Journal of Survey Statistics and Methodology
        \item Quality Engineering
        \item Science Advances
        \item Technometrics
        \item ReWorDS21
        \item WSDS: PrivateNLP
    \end{itemize}
\end{multicols}

\underline{\textbf{\large Advisory Committee:}}\normalsize

\begin{itemize}
    \item Future of Privacy Forums \hfill Jan. 2020 - Present
    \item Census Scientific Advisory Committee \hfill April 2022 - April 2025
    \item 2020 Differential Privacy Temporal Map Challenge \hfill Oct. 2020 - May 2021
    \item 2018 NIST Differential Privacy Synthetic Data Challenge \hfill Oct. 2018 - May 2019
    \item University of Notre Dame College of Science Council \hfill Aug. 2015 - July 2017
    % Graduate Student Representative
\end{itemize}

\professionalspace
\underline{\textbf{\large Program Committee:}}\normalsize

\textbf{Symposium on Data Science and Statistics}
\begin{itemize}
    \item Past-Chair \hfill 2023
    \item Chair \hfill 2022
    \item Vice Chair \hfill 2021
    \item Co-organizer of the Computational Statistics Track \hfill 2020
\end{itemize}
\leadershipspace
\textbf{ACM-IMS Foundations of Data Science} \hfill Jan. 2020 - Oct. 2020

\professionalspace
\underline{\textbf{\large Professional Society Committee:}}\normalsize

\textbf{American Statistical Association} \hfill Feb. 2014 - Present
    \begin{itemize}
        \item Section on Statistical Computing \hfill 2020 - 2025
        \begin{itemize}
            \item Chair \hfill 2023 - 2025
            \item Secretary/Treasurer \hfill 2020 - 2021
        \end{itemize}
        \item Chair for the Government Statistics Section\hfill 2022 - 2024
        \item Committee on Privacy and Confidentiality \hfill 2022 - 2024
        \item Award Committee Member for the Statistics in Defense and National Security Section \hfill 2021 - 2023
        \item Program Chair for the Section on Statistics in the Physical \& Engineering Sciences \hfill 2020 - 2021
        \item Committee on Career Development \hfill 2019 - 2021
        \begin{itemize}
            \item Chair \hfill 2021
            \item Vice-Chair \hfill 2020
        \end{itemize}
    \end{itemize}
    
\leadershipspace
\textbf{Caucus for Women in Statistics} \hfill July 2016 - Dec. 2020
\begin{itemize}
    \item Website Assistant \hfill Jan. 2019 - Dec. 2020
    \item Membership Chair \hfill July 2016 - Dec. 2018
\end{itemize}

\leadershipspace
\textbf{Association for Women in Science - University of Notre Dame Chapter} \hfill Aug. 2013 - May 2018
\begin{itemize}
    \item Social Media Chair \hfill 2016 - 2017
    \item President \hfill 2015 - 2016
    \item Vice President \hfill 2014 - 2015
\end{itemize}
\textit{Chapter awards won while in leadership roles:}
\begin{itemize}
    \item Star Chapter Award \hfill 2014 - 2015, 2015 - 2016, 2016 - 2017
    \item Graduate Life Grant \hfill 2015, 2016
\end{itemize}

\leadershipspace
\textbf{Society of Physics Students (SPS) - Idaho State University Chapter} \hfill Aug. 2008 - May 2013

\begin{itemize}
    \item President \hfill 2010 - 2011
    \item Secretary \hfill 2008 - 2010
\end{itemize}
\textit{Chapter awards won while in leadership roles:}
\begin{itemize}
    \item Outstanding Chapter Zone 15 \hfill 2009, 2010, \&2011
    \item Blake Lily Award \hfill 2011
    \item Marsh White Award \hfill 2009 \& 2011
\end{itemize}

\leadershipspace
\textbf{Mathematics and Computer Science Club - Idaho State University} \hfill Aug. 2009 - May 2013
\begin{itemize}
    \item Treasurer \hfill 2013
    \item Vice President \hfill 2010 - 2012
    \item President \hfill 2009 - 2010
\end{itemize}

\professionalspace
\underline{\textbf{\large Award and Election Nomination Committee:}}\normalsize

\begin{itemize}
    \item Justice, Equity, Diversity, and Inclusion Outreach Group \hfill 2022
    % \item ASA Government Statistical Section Jeanne E Griffith Mentoring Award \hfill 2022
    \item ASA Statistics in Defense and National Security Section \hfill 2021 \& 2022\\ Distinguished Achievement Award
    % Graduate Student Representative
\end{itemize}

\newpage
% \professionalspace
\underline{\textbf{\large Conference Session Organizer:}}\normalsize

\begin{itemize}\setlength\itemsep{2pt}
    \item Aug. 2022. \textit{Expanding Access to Administrative and Survey Data for Public Policy Decision Making}. Joint Statistical Meetings, Washington DC. 
    \item April 2022. \textit{Advancing Data Privacy-Preserving Methodologies}. Joint Mathematics Meetings, Virtual.  
     \item Nov. 2020. \textit{Discussion on ``Disclosure Control Practices on BLS Administrative Data''}. Annual Conference on Taxation, Virtual.   
    \item Aug. 2020. \textit{Data Challenges: Innovating Diverse Solutions}. Joint Statistical Meetings, Virtual.
    \item June 2020. \textit{Differential Privacy: What is it?} SIAM Conference on Mathematics of Data Science, Virtual.
    \item July 2019. \textit{Statistics Impacting Challenges in Academia, Industry, and Government}. Joint Statistical Meetings at Denver, CO.
\end{itemize}

\professionalspace
\underline{\textbf{\large Conference and Seminar Service}}\normalsize

\outreachspace
\textbf{Networking like a Pro: A Guided Networking Session} \hfill \textit{Aug. 2022}\\
\textit{Volunteer} - Assisted with the organization of a guided networking session/workshop for the 2022 Joint Statistical Meetings.

\outreachspace
\textbf{Reaching Your Networking Peak: A Guided Virtual Networking Session} \hfill \textit{Aug. 2021}\\
\textit{Volunteer} - Assisted with the organization of a virtual guided networking session/workshop for the 2021 Joint Statistical Meetings.

\outreachspace
\textbf{2021 and 2022 ASA DataFest} \hfill \textit{April 2021 and 2022}\\
\textit{Judge} - Evaluated the student team presentations for the 2021 ASA DataFest hosted by Bridgewater State University, Bryant University, UMass Dartmouth, and Stonehill College.

\outreachspace
\textbf{Reaching Your Networking Peak: A Guided Virtual Networking Session} \hfill \textit{Aug. 2020}\\
\textit{Head Organizer} - Organized a virtual guided networking session/workshop for the 2020 Joint Statistical Meetings; Invited Dr. Emma Benn, Robert Santos, and Dr. Karen Price to be the guest speakers as well as over 40 volunteers from academia, industry, and government to help and advise participants on networking.

\outreachspace
\cventry{}{}{Poster Judge for the Following Conferences}{\textnormal{}}{}{
    \vspace{-12pt}
    Los Alamos National Laboratory Student Symposium \hfill Aug. 2019\\
    Joint Statistical Meetings - Social Statistics Section \hfill July 2018 \& 2019\\
    Anita Borg Institute - 2018 Grace Hopper Celebration \hfill Sept. 2018
}

\outreachspace
\textbf{Reaching Your Networking Peak: A Guided Networking Session} \hfill \textit{July 2019}\\
\textit{Head Organizer} - Organized a guided networking session/workshop for the 2019 Joint Statistical Meetings at Denver, CO; Invited Dean Sally Morton to be the main speaker as well as over 20 volunteers from academia, industry, and government to help and advise participants on networking.

\outreachspace
\textbf{Caucus for Women in Statistics - On the Go Mentoring Committee} \hfill \textit{July 2017 - July 2018}\\
\textit{Committee Member} - Provided insight as an early career statistician and updated the On the Go Mentoring website.

\outreachspace
\textbf{2018 Joint Research Conference} \hfill \textit{June 2018}\\
\textit{Session Chair} - Facilitated a session at the 2018 Joint Research Conference.

\outreachspace
\textbf{Regional Women in Science Conference} \hfill \textit{April 2016 - Sept. 2016}\\
\textit{Speaker Committee Chair} - Led the speaker committee in arranging eleven external speakers to be keynotes and panelists; Assisted the conference director in organizing the overall conference such as arranging hotel rooms, marketing, and creating the conference website.

\outreachspace
\textbf{LANL - Applying Scholarships, Fellowships, and Grants Seminar} \hfill \textit{July 2015 \& 2016}\\
\textit{Organizer} - Coordinated a seminar on how to apply for scholarships, fellowships, and grants seminar for the Los Alamos National Laboratory student interns with the Los Alamos Student Programs Manager and Assistant Manager, resulting an attendance of over 60 LANL summer interns.

\outreachspace
\textbf{AWIS-ND STEM Luncheon Series} \hfill \textit{Aug. 2014 - April 2016}\\
\textit{Organizer} - Assisted in organizing the monthly STEM Luncheon Series with an average attendance of over 40, where invited speakers talk about resources on campus or their personal experience being a woman in STEM

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STEM K - 12 Service
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \newpage
\section{STEM K-12 and Beyond Outreach}
\textbf{StatFest 2021} \hfill \textit{Sept. 2021}\\
\textit{Volunteer} - Spoke about how to network in a virtual environment.

\outreachspace
\textbf{Skype a Scientist} \hfill \textit{March 2021}\\
\textit{Speaker} - Led a virtual hands-on activity about how to use technology safely for the East Brunswick Brownie Troop for their Cybersecurity I: Basics badge.

\outreachspace
\textbf{StatFest 2020} \hfill \textit{Sept. 2020}\\
\textit{Volunteer} - Facilitated a roundtable on how to network in a virtual environment.

\outreachspace
\textbf{Digital Discussions: Data4Kids} \hfill \textit{May 2020}\\
\textit{Volunteer} - Presented a virtual hands-on activity about how to collect, visualize, and analyze data for primary and secondary level kids.

\outreachspace
\textbf{Adventures in Science} \hfill \textit{Feb. 2020}\\
\textit{Volunteer} - Presented a hands-on statistics experiment and analysis workshop for middle school students.

\outreachspace
\textbf{Julia Robinson Mathematics Festival} \hfill \textit{March 2019}\\
\textit{Volunteer} - Led the hexaflexagon workshop for middle school students.

\outreachspace
\textbf{Northern New Mexico Expanding Your Horizons} \hfill \textit{Oct. 2018}\\
\textit{Volunteer} - Presented a hands-on statistics experiment and analysis workshop for middle school girls.

\outreachspace
\textbf{St. Joseph County Public Library's Science Alive} \hfill \textit{Feb. 2014, 2015, 2016, \& 2018}\\
\textit{\href{http://sjcpl.lib.in.us/sciencealive/}{Volunteer}} - Created fun science hands-on activities for K-12 students such as digging for dinosaur bones at the annual Science Alive Event at the local library, where over 3,000 children learn how science is fun.

\outreachspace
\textbf{University of Notre Dame Expanding Your Horizons} \hfill \textit{April 2014, 2015, 2016, \& 2017}\\
\textit{\href{http://www.expandingyourhorizons.org/conferences/NotreDame/}{Volunteer}} - Provided insight on being a woman in science for the parents of middle school girls; Presented a data privacy workshop and probability hands-on science activities for middle school girls. 

\outreachspace
\textbf{University of Notre Dame Pi Day 5K} \hfill \textit{March 2015, 2016, \& 2017}\\
\textit{\href{http://www.awis.nd.edu/piday5k}{Co-Founder \& Organizer}} - Organized a 1 mile walk, 5K run, and 10K run as well as facilitated science demos and laboratory tours for the community to raise funds for the Boys and Girls Club, which raised over \$10,000.

% \vspace{2pt}
% \cventry{}{Organizer}{ACMS Department Graduate Student Seminars}{\textnormal{\textit{Aug. 2015 - March 2016}}}{}{\begin{itemize}
% \item Organize bimonthly seminars for the ACMS graduate students to share their research or techniques they have learned, creating a friendly environment for students to meet.\end{itemize}}

\outreachspace
\textbf{Girls on the Run Michiana} \hfill \textit{Jan. 2014 - May 2014}\\
\textit{\href{http://www.girlsontherunmichiana.org/}{Coach}} - Mentored and taught girls in middle school to "inspire [them] to be joyful, healthy, and confident using a fun, experience-based curriculum which creatively integrates running." - Girls on the Run

\outreachspace
\textbf{South Bend Community First Friday Event} \hfill \textit{March 2014 \& Feb. 2015}\\
\textit{\href{http://acms.nd.edu/news/47182-acms-first-friday-mad-about-science/}{Volunteer}} - Performed a probability hands-on activity called Monty Hall with the South Bend Community who attend the First Friday Event to learn more about mathematics and statistics.

\outreachspace
\textbf{Idaho National Laboratory's My Amazing Future Program} \hfill \textit{May 2013}\\
\textit{\href{https://inlportal.inl.gov/portal/server.pt?open=514&objID=1269&mode=2&featurestory=DA_575131}{Instructor}} - Encouraged dozens of young girls to pursue careers in STEM through fun physics demonstrations. 

\outreachspace
\textbf{ISU Physics Department Demonstration Shows} \hfill \textit{Aug. 2008 - May 2013}\\
\textit{Demonstration Assistant} - Assisted in presenting educational demonstration shows for K-12 students throughout Idaho, Nevada, and Utah; reaching out to thousands of children to engage them in science.

\outreachspace
\textbf{Southeastern Idaho Mathematics Counts} \hfill \textit{Feb. 2009, 2010, 2011, 2012, \& 2013}\\
\textit{Set-Up/Grader/Judge} - Assisted the event by setting-up, grading, and judging.

\outreachspace
\textbf{Future Faces of Physics Award Project} \hfill \textit{Aug. 2012 - Nov. 2012}\\
\textit{\href{http://www.spsnational.org/programs/awards/2012/FFoP/ffop_recipients.htm}{Instructor}} - aught a local Native American fourth grade class how to design and build egg launchers; Guided the students in participating at a local competition.

\outreachspace
\textbf{Idaho State University - Pocatello, Dept. of Physics} \hfill \textit{June 2011 \& 2012}\\
\textit{QuarkNet Assistant} - Assisted the instructor in educating Idaho Teachers how to teach certain areas of STEM; Built the science demonstrations and tools the Idaho Teachers used to help understand science concepts.

\outreachspace
\textbf{Annual SPS ISU Chapter Pumpkin Chuck} \hfill \textit{Oct. 2009, 2010, \& 2011}\\
\textit{\href{http://www.idahostatejournal.com/news/local/article_845b6364-cc47-11de-b59c-001cc4c002e0.html}{Head Organizer}} - Organized the event for local high schools and colleges to compete by designing trebuchets or catapults that can fling pumpkins as far and accurate as possible.

\outreachspace
\textbf{Annual SPS ISU Chapter Haunted Laboratory} \hfill \textit{Oct. 2008, 2009, 2010, \& 2011}\\
\textit{\href{http://www.isu.edu/headlines/?p=3408}{Head Organizer/Volunteer}} - Assisted in setting up the Haunted Laboratory to scare children with spooky physics and taught them the science of light and illusion; Collaborated with Kiwanis Club in expanding the Haunted Laboratory to a warehouse to accommodate more children.

\outreachspace
\textbf{Annual ISU Science Olympics} \hfill \textit{March 2010 \& 2011}\\
\textit{Volunteer} - Judged how elementary school students tackled various science competitions and challenges such as building circuits or creating wooden airplanes.

\outreachspace
\textbf{Annual SPS ISU Chapter Science Day in the Mall} \hfill \textit{March 2009 \& 2011}\\
\textit{\href{http://m.idahostatejournal.com/news/local/idaho-state-university-physics-club-receives-national-award/article_1823c468-8600-11e2-94b3-0019bb2963f4.html?mode=image&photo=0}{Head Organizer/Volunteer}} - Celebrated Einstein's Birthday and Pi Day with liquid nitrogen ice cream as well as electricity and magnetism activities for children, reaching hundreds of locals.

\outreachspace
\textbf{Idaho Museum of Natural History at Idaho State University} \hfill \textit{Jan. 2009 - May 2010}\\
\textit{\href{http://imnh.isu.edu/home/index.php/science-trek/}{Science Trek \& Science Snacks Instructor}} - Taught children STEM concepts in physics (such as rockets and optics) through physics demonstrations and hands on activities.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Other Activities
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Non-Profit Activities}

% \textbf{Aquatomics} - USA Masters Swim Group in Los Alamos, NM

% \textbf{Santa Fe Road Riders} - Road Cycling Club in Santa Fe, NM 

% \textbf{Triatomics} - Triathlon Club in Los Alamos, NM


\end{document}
