\documentclass[11pt, letterpaper, roman]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{banking} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
\usepackage[leftmargin=20pt]{etaremune}
\usepackage{multicol}
\usepackage[margin = 1in, paperheight=11in, paperwidth=8.5in]{geometry}
\usepackage{import}
\usepackage[
  backend      = biber,
  doi          = true,
  giveninits   = false,
  maxcitenames = 99,
  isbn         = false,
  url          = false,
  style        = apa
]{biblatex}
\addbibresource{bib/blog.bib}
\addbibresource{bib/book.bib}
\addbibresource{bib/peer.bib}
\addbibresource{bib/preprint.bib}
\addbibresource{bib/report.bib}
\DeclareLanguageMapping{english}{english-apa}

% Page Number
\usepackage{lastpage}
\pagestyle{fancy}
\fancyfoot[R]{\thepage\ / \pageref{LastPage}}

% New Commands
\newcommand{\workspace}{\vspace{3pt}}
\newcommand{\projectspace}{\vspace{8pt}}
\newcommand{\grantspace}{\vspace{8pt}}
\newcommand{\awardspace}{\vspace{3pt}}
\newcommand{\professionalspace}{\vspace{8pt}}
\newcommand{\leadershipspace}{\vspace{5pt}}
\newcommand{\outreachspace}{\vspace{4pt}}

\firstname{Claire}
\familyname{Bowen}
\lfoot{CLAIRE MCKAY BOWEN}

\begin{document}
\vspace{-10pt}
\centerline{\huge{CLAIRE MCKAY BOWEN}}
\vspace{10pt}
\hrule
\vspace{5pt}
\centerline{\small E: claire.mckay.bowen@gmail.com | Web: \href{https://www.clairemckaybowen.com}{www.clairemckaybowen.com} | Updated: \today}
\vspace{5pt}
\hrule

% \section{Executive Summary}
% \begin{itemize}
%     \item Highly motivated applied and computational statistician with an infectious enthusiasm for data privacy and confidentiality research with proven leadership experience.
%     \item 10 years experience developing and evaluating differentially private data synthesis methods.
%      \item Organized STEM Outreach programs for 15 years, reaching out to thousands of K-12 students. 
%     % \vspace{4pt}
%     % \item Fluent in R, R Shiny, HTML5, CSS, and Bootstrap 4.
% \end{itemize}

\section{Education}
\import{sections/}{education}

\section{Professional Experience}

\textbf{Urban Institute} \hfill \textit{Dec. 2019 - Present}\\
    \textit{Senior Fellow and Statistical Methods Group Lead \hfill Jan. 2024 - Present}\\
    \textit{Principal Research Associate and Statistical Methods Group Lead \hfill Oct. 2021 - Dec. 2023}\\
    \textit{Lead Data Scientist, Privacy and Data Security \hfill Dec. 2019 - Sept. 2021}
    \begin{itemize}
        \item Leading a multi-year project with the IRS to create synthetic versions of the income tax return database, assess the quality and privacy guarantee of the generated synthetic data, and develop new methods for researchers to access confidential administrative data safely and securely.
        \item Co-leading a project to design and implement the Secure Transfer, Restricted-Use Data Lake Program that promotes and expands restricted-use Department of Labor data access to facilitate timely, accurate, and informative analysis, research, and program evaluation.
        % \item Managing multiple data privacy and confidentiality projects on generating differentially private synthetic data on employer and employee industry data in rural communities in collaboration with the Bureau of Labor Statistics and Bureau of Economic Analysis.
        \item Leading the Statistical Methods Group that provides consulting services for Urban Institute, such as reviewing proposals, brainstorming ideas, and identifying appropriate statistical analyses.
        % \item Developing a body of work on data privacy and confidentiality communications, which includes blogs, research briefs, and a book.
        \item Develops and hosts training on data privacy and confidentiality concepts and methods for various clients, such as Allegheny County and Bureau of Economic Analysis.
        \item Designed an interactive dashboard to assess and evaluate the 2020 Decennial Census population results in collaboration with Massive Data Institute at Georgetown University.
        \item Created a set of tools and resources on how to virtually teach kids about data, data science, and data visualization for 3rd-12th grade teachers, resulting in multiple publications.
    \end{itemize}

\workspace

\textbf{Stonehill College - School of Business} \hfill \textit{June 2022 - Present}\\
\textit{Adjunct Professor}
\begin{itemize}
    \item Teaching duties included preparing a syllabus, creating a new course, lecturing, assigning homework, writing exams, and holding office hours.
\end{itemize}

\workspace 

\textbf{Los Alamos National Laboratory} \hfill \textit{June 2018 - Dec. 2019}\\
\textit{Postdoctoral Research Associate}
% \underline{Advisors}: Dr. Joanne Wendelberger and Dr. Earl Lawrence
\begin{itemize}
        \item Evaluated various differentially private data synthesis methods and quality metric algorithms to assess practical applications.
        \item Developed new methods of functional data analysis, human-in-the-loop, and uncertainty quantification for iterative design.
        \item Investigated the reliability of computer hardware such as cosmic ray effects on supercomputers e.g. Trinity (no. 5 fastest supercomputer upon installment).
        \item Analyzed and evaluated Texas Pre-K to college longitudinal education data to identify attributes for success.
\end{itemize}

% \vspace{4pt}
% \cventry{}{Graduate Research Assistant }{U.S. Census Bureau - Suitland, MD}{\textnormal{\textit{Aug. 2016 - Oct. 2016}}}{}
% {\underline{Mentors}: Dr. Tommy Wright and Dr. Martin Klein
% \begin{itemize}
% \item Implemented methods of data privacy and confidentiality to U.S. Census Bureau data; specifically, applying model-based differentially private data synthesis methods.
% \end{itemize}}

% % \vspace{4pt}
% \cventry{}{Graduate Research Assistant}{Los Alamos National Laboratory (LANL) - Los Alamos, NM}{\textnormal{\textit{May 2015 - July 2015}}}{}
% {\underline{Mentors}:  \href{http://www.lanl.gov/expertise/profiles/view/joanne-wendelberger}{Dr. Joanne Wendelberger} and \href{http://www.lanl.gov/expertise/profiles/view/lawrence-ticknor}{Mr. Lawrence Ticknor}
% \begin{itemize}
% \item Improved an in situ method for approximating complex computer simulations, resulting in a publication.
% \item Created a R package and Shiny App of the developed method as additional learning tools for researchers.
% \end{itemize}}

% \vspace{6pt}
% \cventry{}{Probability and Statistics Instructor}{University of Notre Dame - Notre Dame, IN, Dept. of ACMS}{\textnormal{\textit{Jan. 2015 - May 2015}}}{}{
% \begin{itemize}
% \item Teaching duties included preparing a syllabus, lecturing, assigning homework, writing exams, and holding weekly office hours.
% %\begin{itemize}
% %\item \textbf{Spring 2015:} Probability and Statistics for Computer Scientists and Engineers
% %\end{itemize}
% \end{itemize}}

\newpage
\section{Select Publications \& Invited Presentations}
\begin{etaremune}[topsep=0pt, itemsep=4pt, partopsep=0pt, parsep=0pt]

    \item \textbf{Bowen, CMK.} ``Protecting Your Privacy in a Data-Driven World.'' (Nov. 2021) \textit{Routledge-CRC Press}, American Statistical Association-CRC Series on Statistical Reasoning in Science and Society. \textbf{Book}
    
    \item \textbf{Bowen, CMK.}, Bryant, V., Burman, L., Khitatrakun, S., McClelland, R., Mucciolo, L., Pickens, M., and Williams, A. (2022) ``Synthetic Individual Income Tax Data: Promises and Challenges.'' \textit{National Tax Journal}, 75(4), 767-790.
    
    \item \textbf{Bowen, CMK} and Garfinkel, S. (2021) ``The Philosophy of Differential Privacy.'' \textit{Notices of the American Mathematical Society}, 68(10), pages 1727-1739.\\
    doi: 10.1090/noti2363

    \item \textbf{Bowen, CMK.} and Snoke, J. (2021) ``Comparative Study of Differentially Private Synthetic Data Algorithms from the NIST PSCR Differential Privacy Synthetic Data Challenge.'' \textit{Journal of Privacy and Confidentiality}, 11 (1).\\
    doi: 10.29012/jpc.748

    \item \textbf{Bowen, CMK.} and Liu, F. (2020) ``Comparative Study of Differentially Private Data Synthesis Methods.'' \textit{Statistical Science}, 35(2):280-307.

\end{etaremune}

\rule{\textwidth}{0.1pt}
\begin{etaremune}[topsep=0pt, itemsep=4pt, partopsep=0pt, parsep=0pt]
\smallskip
    
    \item Feb. 2023. \textit{The Art of Data Privacy}. Stonehill College, Easton, Massachusetts.
    
    \item Jan. 2023. \textit{The Future of Data Privacy Methods: Connecting the challenges and opportunities in the Federal Statistical System}. Links Lecture (Connector), Virtual.

    \item July 2022. \textit{Comparative Study of Differentially Private Data Synthesis Methods}. International Society for Bayesian Analysis World Meeting, Bonaventure, Montreal, Quebec, Canada.

    \item April 2022. \textit{Advancing Data Privacy-Preserving Methodologies}. Joint Mathematics Meetings, Virtual. \textbf{Session organizer and presenter.}
    
    \item Feb. 2022. \textit{Personal Privacy and the Public Good}. Association for the Advancement of Artificial Intelligence Workshop of Privacy Preserving Artificial Intelligence. \textbf{Keynote}
  
\end{etaremune}

\section{Select Grants \&  Fellowships}

    \cventry{}{Chief Evaluation Office | \$524,164}{Department of Labor}{\textnormal{\hspace{-1.5cm}\textit{Sept. 2022 - Sept. 2025}}}{}
    { 
        \underline{Project:} Disclosure Protection for the Department of Labor's Restricted-Use Data Access Program\\
        \underline{Role:} Co-Principal Investigator
    }

    \vspace{4pt}
    \cventry{}{Economic Institutions, Behavior, and Performance | Grant No: G-2022-17149 | \$500,000}{Alfred P. Sloan Foundation}{\textnormal{\hspace{-1.5cm}\textit{May 2022 - April 2025}}}{}
    { 
        \underline{Project:} Build and Improve Synthetic Datasets Based on Administrative Tax Data\\
        \underline{Role:} Principal Investigator
    }

    \vspace{4pt}    
    \cventry{}{NSF National Center for Science and Engineering Statistics | \$1.5 million}{National Science Foundation}{\textnormal{\textit{April 2022 - March 2025}}}{}
    {
        \underline{Project:} Building a Validation Server for Administrative Tax Data | 
        \underline{Role:} Principal Investigator
        % PI: Claire McKay Bowen, Co-PIs: Leonard Burman and Graham MacDonald
    }
    
    \vspace{4pt}
    \cventry{}{Regional Income Division | \$250,000}{Bureau of Economic Analysis}{\textnormal{\textit{Sept. 2021 - Dec. 2022}}}{}
    {
        Data Privacy Education Materials and Training | 
        \underline{Role:} Principal Investigator
        % PI: Claire McKay Bowen, Co-PI: Aaron R. Williams
    }

    \vspace{4pt}
    \cventry{}{National Science Foundation | Grant No. DGE-1313583 | \$138,000}{National Science Foundation Graduate Research Fellowship}{\textnormal{\textit{May 2015}}}{}{}

% \vspace{4pt}
%     \cventry{}{Microsoft | \$17,000}{Microsoft Graduate Women's Fellowship}{\textnormal{\textit{Feb. 2014}}}{}{}

\end{document}
