%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Publications
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent\underline{\textbf{Book(s)}}

\begin{etaremune}[topsep=0pt, itemsep=0pt, partopsep=0pt, parsep=0pt]
  \item \textbf{Bowen, CMK.} ``Protecting Your Privacy in a Data-Driven World.'' (Nov. 2021) \textit{Routledge-CRC Press}, American Statistical Association-CRC Series on Statistical Reasoning in Science and Society.
\end{etaremune}

\vspace{6pt}
\noindent\underline{\textbf{Refereed Publications}}
\vspace{4pt}
\begin{etaremune}[topsep=0pt, itemsep=2pt, partopsep=0pt, parsep=0pt]
    \item Williams, A. R., and \textbf{Bowen, CMK}. (2023) ``The Promise and Limitations of Formal Privacy.'' to appear in \textit{Wiley Interdisciplinary Reviews Computational Statistics}.
    
    \item \textbf{Bowen, CMK.}, Bryant, V., Burman, L., Khitatrakun, S., McClelland, R., Mucciolo, L., Pickens, M., and Williams, A. (2022) ``Synthetic Individual Income Tax Data: Promises and Challenges.'' \textit{National Tax Journal}, 75(4), 767-790.
    
    \item \textbf{Bowen, CMK.}, Bryant, V., Burman, L., Czajka, J., Khitatrakun, S., MacDonald, G., McClelland, R., Mucciolo, L., Pickens, M., Ueyama, K., Williams, A., Wissoker, D., and Zwiefel, N. (2022) ``Synthetic Individual Income Tax Data: Methodology, Utility, and Privacy Implications.'' \textit{Privacy in Statistical Databases: International Conference, PSD 2022, Paris, France, September 21–23, 2022}, Proceedings (pp. 191-204). Cham: Springer International Publishing.
    
    \item Garfinkel, S. and \textbf{Bowen, CMK} (2022) ``Preserving Privacy While Sharing Data.'' \textit{MIT Sloan Management Review}, 63 (3), 1-4.
    
    \item \textbf{Bowen, CMK} and Garfinkel, S. (2021) ``The Philosophy of Differential Privacy.'' \textit{Notices of the American Mathematical Society}, 68(10), pages 1727-1739.\\
    doi: 10.1090/noti2363
    
    \item \textbf{Bowen, CMK.} and Snoke, J. (2021) ``Comparative Study of Differentially Private Synthetic Data Algorithms from the NIST PSCR Differential Privacy Synthetic Data Challenge.'' \textit{Journal of Privacy and Confidentiality}, 11(1).\\
    doi: 10.29012/jpc.748

    \item \textbf{Bowen, CMK.} and Liu, F. (2020) ``Comparative Study of Differentially Private Data Synthesis Methods.'' \textit{Statistical Science}, 35(2), pages 280-307.
\end{etaremune}

% \newpage
\vspace{4pt}
\noindent\underline{\textbf{Articles, Editorials, and Other Publications not peer reviewed}}
\vspace{4pt}
\begin{etaremune}[topsep=0pt, itemsep=2pt, partopsep=0pt, parsep=0pt]
    \item \textbf{Bowen, CMK}. and Snoke, J. (2023) ``Do No Harm Guide: Applying Equity Awareness in Data Privacy Methods.'' \textit{Urban Institute}.

    \item \textbf{Bowen, CMK}. Williams, A. R., Pickens, M. (2022) ``Decennial Disclosure: An Explainer on Formal Privacy and the TopDown Algorithm.'' \textit{Urban Institute}.
    
    \item Morrison, G., and \textbf{Bowen, CMK}. (2022) ``Internet First or Internet Choice? Identifying Factors to Predict Low Self-Response Rates on the 2020 Census.'' \textit{Urban Institute}.
        
    \item \textbf{Bowen, CMK.} (2021) ``Personal Privacy and the Public Good: Balancing Data Privacy and Data Utility.'' \textit{Urban Institute}.
    
    \item \textbf{Bowen, CMK.}, Narayanan, A., Scally, C. (2021) ``Using Differential Privacy to Advance Rural Economic Development: Applying Data Privacy and Confidentiality Methods to Industry Employment Data.'' \textit{Urban Institute}.
\end{etaremune}