%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Research Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{Safe Data Technologies} \hfill \textit{2020 - Present}\\
\textit{Principal Investigator}\\ 
\textit{Arnold Ventures, National Science Foundation, Alfred P. Sloan Foundation | \$3 million}

Leads the multi-year project that consists of over 25 people (internal and external collaborators) organized into three subteams and manages all the administrative aspects of the projects. Leads in innovating and improving state-of-the-art data privacy and confidentiality methods on the IRS tax administrative data.

\projectspace
\textbf{Department of Labor's Restricted-Use Data Access Program } \hfill \textit{2022 - Present}\\
\textit{Co-Principal Investigator | U.S. Department of Labor | \$1,524,164}

Co-leads a federal contract that aims to design and implement the Restricted-Use Data Access Program that will safely promote and expand restricted-use of U.S. Department of Labor data access to facilitate timely, accurate, and informative analysis, research, and program evaluation. Lead design and implementation of the disclosure review process. 

\projectspace
\textbf{Do No Harm Guide Vol 2} \hfill \textit{2022 - 2023}\\
\textit{Key Personnel | Tableau Foundation | \$358,432}

Created and wrote one of the four sequels to the ``Do No Harm Guide'' series on applying equity awareness to data privacy methods that includes a literature review, interviews with experts, and illustrative examples.

\projectspace
\textbf{Data Privacy Education Materials and Training } \hfill \textit{2021 - 2022}\\
\textit{Principal Investigator | U.S. Bureau of Economic Analysis | \$250,000}

Led a federal contract to implement synthetic data generation and differential privacy techniques to economic data, tabulations of IRS Schedule C and Form 1065 data. Guided the creation of the educational materials and computational resources through a six-session course series that will empower Bureau of Economic Analysis staff to make informed decisions when selecting data privacy and confidentiality methods.

\projectspace
\textbf{Decennial Dashboard} \hfill \textit{2020 - 2021}\\
\textit{Co-Principal Investigator | Tableau Foundation | \$470,000}

Assisted in designing and developing an interactive dashboard to assess and evaluate the 2020 Decennial Census population results in collaboration with Georgetown University Massive Data Institute. Led in the evaluation of the data privacy impacts on the data.

\projectspace
\textbf{Comparative Study of DIfferentially Private Synthetic Data } \hfill \textit{2019 - 2020}\\
\textit{Principal Investigator | NIST Public Safety Communications Research | \$100,000}

Led the comparative study on various data privacy methods that won a data challenge hosted by the National Institute of Standards and Technology to provide recommendations based on a wide range of quality metrics for the best candidate methods. 