%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Service
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\underline{\textbf{\large National Professional Memberships:}}\normalsize
\begin{itemize}
    \item American Statistical Association \hfill Feb. 2014 - Present
    \item Association of Public Data Users \hfill Jan. 2023 - Present
    \item Caucus for Women in Statistics \hfill July 2016 - Present
    \item Institute of Mathematical Statistics \hfill Sept. 2019 - Present
    \item International Society for Bayesian Analysis \hfill Feb. 2022 - Present
\end{itemize}

\professionalspace
\underline{\textbf{\large Advisory Committees:}}\normalsize
\begin{itemize}
    \item Future of Privacy Forums \hfill Jan. 2020 - Present
    \item Census Scientific Advisory Committee \hfill April 2022 - April 2025
    \item Strategic Advice Team for the Digital Footprints Investment \hfill Jan. 2023 - Dec. 2024
    \item CNSTAT Panel: Approaches for Data Governance and Protecting Privacy \hfill Oct. 2022 - Jan. 2024
    \begin{itemize}
        \item Case Study Subgroup Chair
    \end{itemize}
    \item 2020 Differential Privacy Temporal Map Challenge \hfill Oct. 2020 - May 2021
    \item 2018 NIST Differential Privacy Synthetic Data Challenge \hfill Oct. 2018 - May 2019
    \item University of Notre Dame College of Science Council \hfill Aug. 2015 - July 2017
    % Graduate Student Representative
\end{itemize}

\professionalspace
\underline{\textbf{\large Award and Election Nomination Committees:}}\normalsize
\begin{itemize}
    \item Justice, Equity, Diversity, and Inclusion Outreach Group \hfill 2022
    \item ASA Statistics in Defense and National Security Section \hfill 2021 - 2023\\ Distinguished Achievement Award
\end{itemize}

\professionalspace
% \newpage
\underline{\textbf{\large Editorial and Other Peer-Review Activities:}}\normalsize

\textbf{Editorial Boards:}
\begin{itemize}
    \item Board Member - Significance Magazine \hfill August 2022 - July 2025
    \item Editor - CHANCE \hfill Jan. 2024 - present
    \item Associate Editor - Technometrics \hfill Jan. 2022 - Dec. 2024
    \item Guest Editor - Journal of Data Science \hfill June 2022 - May 2023
\end{itemize}

\vspace{5pt}
\textbf{Grant and Fellowship Proposal Reviewer:}
\begin{itemize}
    \item Alfred P. Sloan \hfill 2021
    \item Grace Hopper Celebration Scholarship \hfill 2020
    \item National Science Foundation \hfill 2019 - 2023
\end{itemize}

\vspace{5pt}
\textbf{Journal Peer Review:}
\vspace{-10pt}
\begin{multicols}{2}
    \begin{itemize}
        \item ACM-IMS Foundations of Data Science
        \item The American Statistician
        \item BMC Medical Informatics and Decision Making
        \item Harvard Data Science Review
        \item IEEE Transactions on Information Forensics \& Security
        \item Journal of Privacy and Confidentiality
        \item Journal of Royal Statistical Society - Series A
        \item Journal of Statistical Theory and Practice
        \item Journal of Survey Statistics and Methodology
        \item Quality Engineering
        \item Science Advances
        \item Statistical Science
        \item Technometrics
        \item ReWorDS21
        \item WSDS: PrivateNLP
    \end{itemize}
\end{multicols}

\vspace{-2pt}
\textbf{Report Reviewer:}
\begin{itemize}
    \item Committee on National Statistics of the National Academies of Sciences, Engineering, and Medicine
\end{itemize}

\vspace{5pt}
\textbf{Book Reviewer:}
\vspace{-10pt}
\begin{multicols}{2}
    \begin{itemize}
        \item CRC Press
        \item MIT Press
    \end{itemize}
\end{multicols}

% \professionalspace
\underline{\textbf{\large Program Committees:}}\normalsize

\textbf{Privacy and Public Policy Conference}
\begin{itemize}
    \item Co-Program Chair and Founder \hfill Sept. 2023 - Sept. 2024
\end{itemize}
\professionalspace

\textbf{NISS IOF Workshop:} \hfill May 2022 - April 2023\\
\textit{Advancing Demographic Equity with Privacy-Preserving Methodologies}
\professionalspace

\textbf{Symposium on Data Science and Statistics}
\begin{itemize}
    \item Vice Chair, Chair, and Past-Chair \hfill June 2021 - June 2023
    \item Co-organizer of the Computational Statistics Track \hfill June 2020
\end{itemize}
\leadershipspace
\textbf{ACM-IMS Foundations of Data Science} \hfill Jan. 2020 - Oct. 2020

\professionalspace
\underline{\textbf{\large Professional Society Committees:}}\normalsize

\textbf{American Statistical Association} \hfill Feb. 2014 - Present
    \begin{itemize}
        \item Section on Statistical Computing \hfill 2020 - 2025
        \begin{itemize}
            \item Chair \hfill 2023 - 2025
            \item Secretary/Treasurer \hfill 2020 - 2021
        \end{itemize}
        \item Chair for the Government Statistics Section\hfill 2022 - 2024
        \item Committee on Privacy and Confidentiality \hfill 2022 - 2024
        \item Program Chair for the Section on Statistics in the Physical \& Engineering Sciences \hfill 2020 - 2021
        \item Committee on Career Development \hfill 2019 - 2021
        \begin{itemize}
            \item Chair \hfill 2021
            \item Vice-Chair \hfill 2020
        \end{itemize}
    \end{itemize}

\textbf{Association of Public Data Users} \hfill Jan. 2022 - Present
    \begin{itemize}
        \item At-Large Member \hfill Jan. - Dec. 2024
    \end{itemize}
    
\leadershipspace
\textbf{Caucus for Women in Statistics} \hfill July 2016 - Dec. 2020
\begin{itemize}
    \item Website Assistant \hfill Jan. 2019 - Dec. 2020
    \item Membership Chair \hfill July 2016 - Dec. 2018
\end{itemize}

\leadershipspace
\textbf{Association for Women in Science - University of Notre Dame Chapter} \hfill Aug. 2013 - May 2018
\begin{itemize}
    \item Social Media Chair \hfill 2016 - 2017
    \item President \hfill 2015 - 2016
    \item Vice President \hfill 2014 - 2015
\end{itemize}
\textit{Chapter awards won while in leadership roles:}
\begin{itemize}
    \item Star Chapter Award \hfill 2014 - 2015, 2015 - 2016, 2016 - 2017
    \item Graduate Life Grant \hfill 2015, 2016
\end{itemize}

\leadershipspace
\textbf{Society of Physics Students - Idaho State University Chapter} \hfill Aug. 2008 - May 2013

\begin{itemize}
    \item President \hfill 2010 - 2011
    \item Secretary \hfill 2008 - 2010
\end{itemize}
\textit{Chapter awards won while in leadership roles:}
\begin{itemize}
    \item Outstanding Chapter Zone 15 \hfill 2009, 2010, \& 2011
    \item Blake Lily Award \hfill 2011
    \item Marsh White Award \hfill 2009 \& 2011
\end{itemize}

\leadershipspace
\textbf{Mathematics and Computer Science Club - Idaho State University} \hfill Aug. 2009 - May 2013
\begin{itemize}
    \item Treasurer \hfill 2013
    \item Vice President \hfill 2010 - 2012
    \item President \hfill 2009 - 2010
\end{itemize}

% \newpage
\professionalspace
\underline{\textbf{\large Conference Session Organizer:}}\normalsize

\begin{itemize}\setlength\itemsep{2pt}
    \item Aug. 2022. \textit{Expanding Access to Administrative and Survey Data for Public Policy Decision Making}. Joint Statistical Meetings, Washington DC. 
    \item April 2022. \textit{Advancing Data Privacy-Preserving Methodologies}. Joint Mathematics Meetings, Virtual.  
     \item Nov. 2020. \textit{Discussion on ``Disclosure Control Practices on BLS Administrative Data''}. Annual Conference on Taxation, Virtual.   
    \item Aug. 2020. \textit{Data Challenges: Innovating Diverse Solutions}. Joint Statistical Meetings, Virtual.
    \item June 2020. \textit{Differential Privacy: What is it?} SIAM Conference on Mathematics of Data Science, Virtual.
    \item July 2019. \textit{Statistics Impacting Challenges in Academia, Industry, and Government}. Joint Statistical Meetings at Denver, CO.
\end{itemize}

\professionalspace
\underline{\textbf{\large Conference and Seminar Service}}\normalsize

\outreachspace
\textbf{NISS IOF Workshop} \hfill \textit{Jan. 2023}\\
% on Advancing Demographic Equity with Privacy-Preserving Methods
\textit{Co-Head Organizer} - Organized a two-day workshop on data privacy and equity in Washington DC.

\outreachspace
\textbf{Networking like a Pro: A Guided Networking Session} \hfill \textit{Aug. 2022}\\
\textit{Volunteer} - Assisted with the organization of a guided networking session/workshop for the 2022 Joint Statistical Meetings.

\outreachspace
\textbf{Reaching Your Networking Peak: A Guided Virtual Networking Session} \hfill \textit{Aug. 2021}\\
\textit{Volunteer} - Assisted with the organization of a virtual guided networking session/workshop for the 2021 Joint Statistical Meetings.

\outreachspace
\textbf{Reaching Your Networking Peak: A Guided Virtual Networking Session} \hfill \textit{Aug. 2020}\\
\textit{Head Organizer} - Organized a virtual guided networking session/workshop for the 2020 Joint Statistical Meetings; Invited Dr. Emma Benn, Robert Santos, and Dr. Karen Price to be the guest speakers as well as over 40 volunteers from academia, industry, and government to help and advise participants on networking.

\outreachspace
\cventry{}{}{Poster Judge for the Following Conferences}{\textnormal{}}{}{
    \vspace{-12pt}
    Los Alamos National Laboratory Student Symposium \hfill Aug. 2019\\
    Joint Statistical Meetings - Social Statistics Section \hfill July 2018 \& 2019\\
    Anita Borg Institute - 2018 Grace Hopper Celebration \hfill Sept. 2018
}

\outreachspace
\textbf{Reaching Your Networking Peak: A Guided Networking Session} \hfill \textit{July 2019}\\
\textit{Head Organizer} - Organized a guided networking session/workshop for the 2019 Joint Statistical Meetings at Denver, CO; Invited Dean Sally Morton to be the main speaker as well as over 20 volunteers from academia, industry, and government to help and advise participants on networking.

\outreachspace
\textbf{Caucus for Women in Statistics - On the Go Mentoring Committee} \hfill \textit{July 2017 - July 2018}\\
\textit{Committee Member} - Provided insight as an early career statistician and updated the On the Go Mentoring website.

\outreachspace
\textbf{2018 Joint Research Conference} \hfill \textit{June 2018}\\
\textit{Session Chair} - Facilitated a session at the 2018 Joint Research Conference.

\outreachspace
\textbf{Regional Women in Science Conference} \hfill \textit{April 2016 - Sept. 2016}\\
\textit{Speaker Committee Chair} - Led the speaker committee in arranging eleven external speakers to be keynotes and panelists; Assisted the conference director in organizing the overall conference such as arranging hotel rooms, marketing, and creating the conference website.

\outreachspace
\textbf{LANL - Applying Scholarships, Fellowships, and Grants Seminar} \hfill \textit{July 2015 \& 2016}\\
\textit{Organizer} - Coordinated a seminar on how to apply for scholarships, fellowships, and grants seminar for the LANL student interns with the Los Alamos Student Programs Manager and Assistant Manager, resulting an attendance of over 60 LANL summer interns.

\outreachspace
\textbf{AWIS-ND STEM Luncheon Series} \hfill \textit{Aug. 2014 - April 2016}\\
\textit{Organizer} - Assisted in organizing the monthly STEM Luncheon Series with an average attendance of over 40, where invited speakers talk about resources on campus or their personal experience being a woman in STEM
