%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Presentations
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\underline{\textbf{\large Panels}}\normalsize
\vspace{4pt}
\begin{etaremune}[topsep=0pt, itemsep=2.5pt, partopsep=0pt, parsep=0pt]
    \item Oct. 2023. \textit{Measuring the Health of the Federal Statistical System}. FCSM Research \& Policy Conference at College Park Marriott Hotel \& Conference Center, Hyattsville, MD.
    
    \item Oct. 2022. \textit{Growing Statistical Careers}. Women in Statistics and Data Science Conference at St. Louis, MO. \textbf{Moderator}
    
    \item Aug. 2022. \textit{Virtual Lunch: A Conversation with Urban Authors}. Urban Institute, Virtual.
    
    \item Oct. 2021. \textit{Wrapping Up and Moving On: Advice for the Final Stretch of Graduate School}. Women in Statistics and Data Science Conference, Virtual.
    
    \item Oct. 2021. \textit{Which Path Should I Choose? A Discussion of Employment in Academia, Industry, Government, and Nonprofits}. Women in Statistics and Data Science Conference, Virtual.
    
    \item Oct. 2020. \textit{Data Governance in the Era of Big Data}. Women in Statistics and Data Science Conference, Virtual.
    
    \item April 2020. \textit{Postdoc Positions}. Virtual Office Hours, webinar hosted by the American Statistical Association Committee on Career Development. \textbf{Moderator}
    
    \item Oct. 2018. \textit{Implicit Bias and Power Dynamics: How We Can Change the Culture}. Women in Statistics and Data Science Conference, Cincinnati, OH.

    \item March 2015. \textit{Graduate School Advice Panel}.  Regional Society of Women Engineers Conference, Notre Dame, IN.
    
    \item Sept. 2014. \textit{Graduate School Advice Panel}.  University of Notre Dame Career Center, Notre Dame, IN.
    
% \newpage
\vspace{6pt}
\hspace{-0.30in}\underline{\textbf{\large Oral Presentations}}\normalsize
    \item Oct. 2023. \textit{Do No Harm Guide: Applying Equity Awareness in Data Privacy Methods}. FCSM Research \& Policy Conference at College Park Marriott Hotel \& Conference Center, Hyattsville, MD.
    
    \item June 2023. \textit{Do No Harm Guide: Applying Equity Awareness in Data Privacy Methods}. International Chinese Statistical Association Applied Statistics Symposium, Ann Arbor, MI.
    
    \item Sept. 2022. \textit{Synthetic Individual Income Tax Data: Methodology, Utility, and Privacy Implications}. International Conference on Privacy in Statistical Databases, Paris, France.
    
    \item April 2022. \textit{Protecting Your Privacy in a Data-Driven World}. Statistical Methods Group Brown Bag, the Urban Institute.
    
    \item Feb. 2022. \textit{Urban Formatting in LaTeX.} Urban Seed Fund Symposium, the Urban Institute.

    \item Nov. 2021. \textit{Data Science and Public Policy}. ASA Student Chapter at University of Georgia ASA Student Chapter Seminar, Virtual.
    
    \item Nov. 2021. \textit{Synthetic Public Use File of Administrative Tax Data: Methodology, Utility, and Privacy Implications}. Federal Committee on Statistical Methodology Conference, Virtual.
    
    \item Sept. 2021. \textit{Validation Server Project: SmartNoise Use Case}. OpenDP Community Meeting, Virtual.
    
    \item Sept. 2021. \textit{Networking Prep: How to Network in a Virtual Landscape}. StatFest 2021, Virtual.
    
    \item Nov. 2020. \textit{Discussion on ``Disclosure Control Practices on BLS Administrative Data''}. Annual Conference on Taxation, Virtual. \textbf{Session organizer and presenter.}
    
    \item Oct. 2020. \textit{Another Invisible Threat: Unequal Privacy Cost of Tracing COVID-19}. Grace Hopper Celebration, Virtual.
    
    \item Sept. 2020. \textit{NSF Graduate and Postdoctoral Fellowships: Opportunities and Advice}. Webinar hosted by ASA Committee on Funded Research.
    
    \item Sept. 2020. \textit{IRS Validation Server Initiative}. Webinar hosted by Internal Revenue Service Statistics of Income Division.
    
    \item Aug. 2020. \textit{Data Challenges: Innovating Diverse Solutions}. Joint Statistical Meetings, Virtual. \textbf{Session organizer and presenter.}
    
    \item July 2020. \textit{Setting Policymaking Priorities on Differential Privacy}. Association of Public Data Users Annual Conference, Virtual.
    
    \item June 2020. \textit{Differential Privacy: What is it?} SIAM Conference on Mathematics of Data Science, Virtual. \textbf{Session organizer and presenter}
    
    \item May 2020. \textit{Data\@Urban Digital Discussions Teaching Data to Kids}. Data\@Urban Digital Discussions, webinar hosted by the Urban Institute.
    
    \item April 2020. \textit{Meet a Statistician: Claire Bowen}. Meet a Statistician Series, webinar hosted by This is Statistics.
    
    \item April 2020. \textit{Optimizing Data to Advance Rural Economic Development}. Fleishman Innovation Award Presentation at the Urban Institute.
    
    \item March 2020. \textit{Social Media}. Caucus for Women in Statistics Lunch and Learn, webinar hosted by the Caucus for Women in Statistics.
    
    \item July 2019. \textit{Iterative Design with Humans-in-the-Loop for Functional Data Analysis}. Joint Statistical Meetings, Denver, CO. 
    
    \item July 2019. \textit{How to Get that Funding: Writing Successful Scholarship Applications}. LANL, Los Alamos, NM.
    
    \item June 2019. \textit{Telling a Visual Story in Big Data}. Science in 3, LANL, Los Alamos, NM. 
    
    \item April 2019. \textit{Telling a Visual Story in Big Data: Case Studies on Interactive Visualizations for Supercomputer Data}. Rising Stars in Computational and Data Sciences Workshop at the University of Texas-Austin, Austin, TX.
    
    \item April 2019. \textit{Do Solar Proton Events Reduce the Number of Faults in Supercomputers?: A Comparative Analysis of Faults during and without Solar Proton Events}. IEEE International Reliability Physics Symposium, Monterrey, California.
    
    \item Sept. 2018. \textit{How to Get that Funding: Writing Successful Scholarship Applications}. Grace Hopper Celebration, Houston, TX.
    
    \item Oct. 2018. \textit{How to Get that Funding: Writing Successful Scholarship Applications}. Women in Statistics and Data Science Conference, Cincinnati, OH.
    
    \item Aug. 2018. \textit{Statistical Tests to Elect Partitions Sequentially (STEPS) and Its Applications in Differentially Private Release and Analysis of Voter Registration Data}. Joint Statistical Meetings, Vancouver, BC in Canada.
    
    \item July 2018. \textit{Creating Your Own Luck at JSM}. Joint Statistical Meetings at Vancouver, BC in Canada.
    
    \item July 2018. \textit{Creating Your Own Luck}. LANL, Los Alamos, NM.
    
    \item July 2018. \textit{How to Get that Funding}. LANL, Los Alamos, NM.
    
    \item February 2018. \textit{Creating Your Own Luck}. University of Notre Dame, Notre Dame, IN.
    
    \item Nov. 2017. \textit{Statistical Tests to Elect Partitions Sequentially (STEPS) and Its Applications in Differentially Private Release and Analysis of Voter Registration Data}. Statistics Seminar Series University of Notre Dame, Notre Dame, IN.
    
    \item Aug. 2017. \textit{Comparative Study of Differentially Private Data Synthesis Methods}. Joint Summer Meeting University of Notre Dame, Notre Dame, IN.
    
    \item Aug. 2017. \textit{Comparative Study of Differentially Private Data Synthesis Methods}. Joint Statistical Meetings, Baltimore, MD.\\
    \textcolor{blue}{2017 JSM Student Paper Award}
    
    \item April 2017. \textit{Comparative Study of Differentially Private Data Synthesis Methods}. Society for Industrial and Applied Mathematics Student Seminar at University of Notre Dame, Notre Dame, IN.
    
    \item May 2017. \textit{Statistical Allocation for Epsilon: A Differentially Private Application and Evaluation on Voter Registration Data}. College of Science - Joint Annual Meeting at University of Notre Dame, Notre Dame, IN.
    
    \item Oct. 2016. \textit{Differentially Private Data Synthesis Partitioning for Big Data}. Regional Women in Science Conference at University of Notre Dame, Notre Dame, IN. 
    
    \item Sept. 2016. \textit{What is Differential Privacy}. Center for Statistical Research Methodology Monthly Group Meeting, US Census Bureau at Suitland, MD. 
    
    \item July 2016. \textit{Differentially Private Data Synthesis Partitioning for Big Data}. Talking to Ourselves, LANL, Los Alamos, NM.
    
    \item July 2016. \textit{Applying Scholarships, Fellowships, and Grants Seminar}. LANL, Los Alamos, NM.
    
    \item March 2016. \textit{Big Brother in Big Data}. Three Minute Thesis Competition at University of Notre Dame, Notre Dame, IN.
    
    \item Sept. 2015. \textit{An In Situ Approach for Approximating Complex Computer Simulations and Identifying Important Time Steps}. New Technologies, New Knowledge - Center for Digital Scholarship Lightning Talks at University of Notre Dame, Notre Dame, IN.
    
    \item Aug. 2015. \textit{Data Privacy via Integration of Data Synthesis and Differential Privacy}. Joint Statistical Meeting at Washington Convention Center, Seattle, WA.
    
    \item July 2015. \textit{An In Situ Approach for Approximating Complex Computer Simulations and Identifying Important Time Steps}. 2015 Computing and Information Technology Student Mini Showcase, LANL, Los Alamos, NM.
    
    \item July 2015. \textit{An In Situ Approach for Approximating Complex Computer Simulations and Identifying Important Time Steps}. T Division Lightning Talks at LANL, Los Alamos, NM.
    
    \item July 2015. \textit{Applying Scholarships, Fellowships, and Grants Seminar}. LANL, Los Alamos, NM.
    
    \item July 2015. \textit{An In Situ Approach for Approximating Complex Computer Simulations and Identifying Important Time Steps}. Talking to Ourselves at LANL, Los Alamos, NM.
    
    \item June 2015. \textit{Data Privacy via Integration of Data Synthesis and Differential Privacy}. Talking to Ourselves, LANL, Los Alamos, NM. 
    
    \item May 2014. \textit{Facilitated Morning Discussion}. Women in Statistics Conference, Cary, NC.
    
    \item March 2014. \textit{Are More of My Patients Experiencing Side Effects than Expected}. Association for Women in Science STEM Luncheon Series at University of Notre Dame, Notre Dame, IN.
    
    \item Dec. 2012. \textit{Differences between Experts and Novices in the Ability to Detect Changes in Images}. Honors Thesis at Idaho State University, Pocatello, ID.
    
    \item April 2012. \textit{Investigating the Mechanisms of the Rho Helicase}. Idaho State University Undergraduate Research Symposium, Pocatello, ID.
    
    \item April 2012. \textit{Investigating the Mechanisms of the Rho Helicase}. Society of Physics Zone 15 Meeting at Brigham Young University - Idaho, Rexburg, ID.
    
    \item March 2011. \textit{The Reflection and Transmission of Physical Optics and Waves in Physics Education Research}. Society of Physics Zone 15 Meeting at Utah State University at Logan, UT.\\
    \textcolor{blue}{Best Oral Presentation}
  
% \newpage
%%%%%%%% Poster
\vspace{8pt}
\hspace{-0.30in}\underline{\textbf{\large Poster Presentations}}\normalsize
    \item July 2019. \textit{Telling a Visual Story in Big Data: Case Studies on Interactive Visualizations for Supercomputer Data}. 21st Meeting of New Researchers in Statistics and Probability at Colorado State University, Fort Collins, CO.
    
    \item May 2019. \textit{Telling a Visual Story in Big Data: Case Studies on Interactive Visualizations for Supercomputer Data}. Spring Research Conference at Virginia Tech, Blacksburg, VA.
    
    \item April 2019. \textit{Telling a Visual Story in Big Data: Case Studies on Interactive Visualizations for Supercomputer Data}. Rising Stars in Computational and Data Sciences Workshop at the University of Texas-Austin, Austin, TX.
    
    \item June 2018. \textit{Noisy Edges and Traits Methods: Differentially Private Data Synthesis Methods for Social Network Data}. 2018 Joint Research Conference, Santa Fe, NM.
    
    \item Oct. 2017. \textit{Statistical Allocation for Epsilon: A Differentially Private Application and Evaluation on Voter Registration Data}. 2017 Women in Statistics and Data Science Conference, La Jolla, CA.
    
    \item Feb. 2017. \textit{Partitioning a Large Simulation as It Runs}. 2017 Women in Mathematics Symposium at Indiana University - Purdue University Indianapolis, Indianapolis, IN.
    
    \item Oct. 2016. \textit{Differentially Private Data Synthesis Partitioning for Big Data}. Women in Statistics and Data Science Conference at Crown Plaza Hotel, Charlotte Executive Park, NC. 
    
    \item April 2016. \textit{Partitioning a Large Simulation as It Runs}. 2016 Graduate Student Union Research Symposium at University of Notre Dame, Notre Dame, IN.\\
    \textcolor{blue}{1st Place - College of Science Division}
    
    \item July 2015. \textit{An In Situ Approach for Approximating Complex Computer Simulations and Identifying Important Time Steps}. 2015 Computing and Information Technology Student Mini Showcase, LANL, Los Alamos, NM.
    
    \item Nov. 2012. \textit{Differences between Experts and Novices in the Ability to Detect Changes in Images}. Sigma Pi Sigma Quadrennial Meeting at Royal Caribbean Hotel, Orlando, FL.
    
    \item April 2012. \textit{Investigating the Mechanisms of the Rho Helicase}. Society of Physics Zone 15 Meeting at Brigham Young University - Idaho, Rexburg, ID.
    
    \item April 2012. \textit{Investigating the Mechanisms of the Rho Helicase}. Undergraduate Research Symposium at Idaho State University, Pocatello, ID.
    
    \item April 2011. \textit{The Reflection and Transmission of Physical Optics and Waves in Physics Education Research}. Undergraduate Research Symposium at Idaho State University, Pocatello. ID.
    
    \item March 2011. \textit{The Reflection and Transmission of Physical Optics and Waves in Physics Education Research}. Society of Physics Zone 15 Meeting at Utah State University, Logan, UT.
\end{etaremune}