%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Presentations
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\underline{\textbf{\large Keynotes}}\normalsize
\vspace{6pt}
\begin{etaremune}[topsep=0pt, itemsep=4pt, partopsep=0pt, parsep=0pt]
    \item Feb. 2022. \textit{Personal Privacy and the Public Good}. Association for the Advancement of Artificial Intelligence Workshop of Privacy Preserving Artificial Intelligence.
    
\vspace{6pt}
\hspace{-0.30in}\underline{\textbf{\large Scientific Meetings}}\normalsize
    \item Aug. 2024. \textit{Government Data of the People, By the People, For the People: Navigating Citizen Privacy Concerns}. Joint Statistical Meetings, Portland, OR.

    \item Aug. 2024. \textit{The Case for Researching Applied Privacy Enhancing Technologies}. Joint Statistical Meetings, Portland, OR.

    \item Aug. 2023. \textit{Do No Harm Guide: Applying Equity Awareness in Data Privacy Methods}. Joint Statistical Meetings, Toronto, Ontario, Canada.
    
    \item Jan. 2023. \textit{Welcome and Introduction}. NISS IOF Workshop on Advancing Demographic Equity with Privacy-Preserving Methodologies, Urban Institute, Washington D.C.
    
    \item Aug. 2022. \textit{The Art of Data Privacy}. IQT Tech Focus Day, Washington D.C.
    
    \item July 2022. \textit{Comparative Study of Differentially Private Data Synthesis Methods}. International Society for Bayesian Analysis World Meeting, Bonaventure, Montreal, Quebec, Canada.
    
    \item June 2022. \textit{Safely Expanding Research Access to Administrative Tax Data}. SPOKES Privacy Technology Conference, Virtual.
    
    \item April 2022. \textit{A Feasibility Study of Differentially Private Summary Statistics and Regression Analyses for Administrative Tax Data}. Noisy Measurements Research Workshop, Rutgers University at New Brunswick, NJ.
    
    \item April 2022. \textit{Advancing Data Privacy-Preserving Methodologies}. Joint Mathematics Meetings, Virtual. \textbf{Session organizer and presenter.}

    \item Sept. 2021. \textit{Generating Synthetic Data for Data Privacy in R}. noRth R, Virtual.

    \item Aug. 2021. \textit{Another Invisible Threat: Unequal Privacy Cost of Tracing COVID-19}. Joint Statistical Meetings, Virtual.
    
    \item July 2021. \textit{Differential Privacy in the Real-World}. American Association for Public Opinion Research Webinar.

    \item June 2020. \textit{Telling a Visual Story in Big Data: Case Studies on Interactive Visualizations for Supercomputer Data}. Symposium on Data Science and Statistics, Virtual.
  
    \item June 2020. \textit{Best Practices for Leading Data Science Efforts in Your Organization}. Symposium on Data Science and Statistics, Virtual.
  
    \item April 2020. \textit{Differential Privacy: What is it?} Women in Data Science Conference, the Virginia Tech at Blacksburg, VA, Virtual.

    \item Aug. 2016. \textit{Differentially Private Data Synthesis Partitioning for Big Data}. Joint Statistical Meetings at McCormick Place, Chicago, IL.
    
    \item Sept. 2015. \textit{Differential Privacy \& the Mosaic Effect}. NSF-National Center for Science and Engineering Statistics Expert Panel on Confidentiality Protection at SRI, Arlington, VA.

\vspace{6pt}
\hspace{-0.30in}\underline{\textbf{\large Seminars}}\normalsize  
    \item June 2024. \textit{Responsibly Represent People in Data: Navigating Data Privacy Challenges in Public Policy}. Washington Statistical Society President's Lecture at Jefferson Auditorium, USDA South Building, Washington, DC.

    \item April 2024. \textit{Responsibly Represent People in Data: Navigating Data Privacy Challenges in Public Policy}. Biostatistics Seminar Series at Boston University, Boston, MA.
    
    \item April 2024. \textit{Responsibly Represent People in Data: Navigating Data Privacy Challenges in Public Policy}.  Data Analytics and Computational Social Science Seminar at University of Massachusetts-Amherst, Amherst, MA.
    
    \item Dec. 2023. \textit{The Art of Data Privacy}. Statistical Computing of the American Statistical Association Webinar, Virtual.

    \item Oct. 2023. \textit{Safe Data Technologies: Safely Expanding Access to Administrative Tax Data}. Statistics Seminar Series at University of Michigan, Ann Arbor, MI.

    \item Sept. 2023. \textit{Navigating Privacy Concerns in the Practice of Statistics: A Necessary Part of the Consulting Toolkit}. Privacy Webinar Series for the Statistical Consulting Section of the American Statistical Association, Virtual.    
    
    \item Sept. 2023. \textit{Safe Data Technologies: Safely Expanding Access to Administrative Tax Data}. Statistics Seminar Series at University of Notre Dame, Notre Dame, IN.
    
    \item Feb. 2023. \textit{The Art of Data Privacy}. Stonehill College, Easton, MA.
    
    \item Jan. 2023. \textit{The Future of Data Privacy Methods: Connecting the challenges and opportunities in the Federal Statistical System}. Links Lecture (Connector), Virtual.
    
    \item Aug. 2022. \textit{Dr. Claire McKay Bowen: From Physics to Public Policy}. Webinar hosted by Technically Private.
    
    \item Aug. 2022. \textit{Protecting Your Privacy in a Data-Driven World}. Webinar hosted by DC AAPOR, Virtual.
    
    \item May 2022. \textit{Protecting Your Privacy in a Data-Driven World}. Epidemiology and Biostatistics Seminar Series at Drexel University, Philadelphia, PA.
    
    \item May 2022. \textit{Data4Kids: Virtually Teaching Kids about Data Science}. Cyberinfrastructure for Network Science Center Research Showcase, Indiana University, Virtual.
    
    \item March 2022. \textit{Protecting Your Privacy in a Data-Driven World}. Webinar hosted by Abt. Associates, Virtual.
    
    \item March 2022. \textit{Safely Expanding Research Access to Administrative Tax Data}. Neyman Seminar Series at University of California Berkeley, Virtual.
    
    \item March 2022. \textit{Protecting Your Privacy in a Data-Driven World}. McDonough School of Business at Georgetown University, Virtual.
    
    \item March 2022. \textit{Dr. Claire McKay Bowen: From Physics to Public Policy}. Journeys in Statistics and Data Science, Penn State University, Virtual.
        
    \item Feb. 2022. \textit{Data Privacy Preserving Applications with R}. Webinar hosted by R-Ladies Baltimore.

    \item Jan. 2022. \textit{Protecting Your Privacy in a Data-Driven World}. Webinar hosted by the Washington Statistical Society, Virtual.
    
    \item Dec. 2021. \textit{Statistics and Data Science at the Urban Institute}. Statistics Seminar at Florida State University, Virtual.
    
    \item Nov. 2021. \textit{Protecting Your Privacy in a Data-Driven World}. Biostatistics Seminar Series at Johns Hopkins University, Baltimore, MD.
    
    \item Sept. 2021. \textit{Protecting Your Privacy in a Data-Driven World}. Statistics Seminar Series at Virginia Tech, Blacksburg, VA. \textcolor{blue}{My 100th Talk}
    
    \item April 2021. \textit{How the Federal Government Can Use Data to Make the Most of the Executive Order on Racial Equity}. Heinz College at Carnegie Mellon University, Virtual.

    \item Feb. 2021. \textit{How Statistics Protects Your Privacy in a World Driven by Data}. STEM Seminar Series, Henderson State University, Virtual.

    \item Nov. 2020. \textit{Data Privacy in the Real World}. Statistics Seminar Series at Bureau of Labor Statistics, Virtual.

    \item Sept. 2020. \textit{Data Privacy in the Real World}. Statistics Seminar Series at University of Pittsburgh, Virtual.
        
    \item Aug. 2020. \textit{Data Privacy in the Real World with Claire McKay Bowen, PhD}. Webinar hosted by DataBasement, SWFL Coders, SWFL PyLadies, Miami PyLadies, and SWFL Data MeetUp.
    
    \item Feb. 2020. \textit{Comparative Study of Differentially Private Synthetic Data Algorithms and Evaluation Standards}. Statistics Colloquia, University of California-Riverside at Riverside, CA.
    
    \item Feb. 2020. \textit{How to Tell a Less Flawed Data Story: Data Analytics, Data Communication, and Data Privacy}. Statistics Seminar at Bryant University, Provenance, RD.
    
    \item Sept. 2019. \textit{Comparative Study of Differentially Private Data Synthesis Methods}. Urban Institute, Washington, D.C.
    
    \item Oct. 2018. \textit{What is Data Science?} Data Science: Overview, Insights, and Path Forward Workshop at University of Texas-El Paso, El Paso, TX.
    
    \item Dec. 2017. \textit{Statistical Tests to Elect Partitions Sequentially (STEPS) and Its Applications in Differentially Private Release and Analysis of Voter Registration Data}. Applied Statistics Group at Lawrence Livermore National Laboratory, Livermore, CA.
    
    \item Oct. 2017. \textit{Statistical Allocation for Epsilon: A Differentially Private Application and Evaluation on Voter Registration Data}. Applied and Computational Statistics Group at National Institute of Standards and Technology, Boulder, CO.
    
    \item Sept. 2017. \textit{Statistical Allocation for Epsilon: A Differentially Private Application and Evaluation on Voter Registration Data}. Statistical Sciences Group at Sandia National Labs, Albuquerque, NM.
    
    \item Sept. 2017. \textit{Statistical Allocation for Epsilon: A Differentially Private Application and Evaluation on Voter Registration Data}. Applied Statistics and Computational Modeling Group at Pacific Northwest National Laboratory, Richland, WA.
    
    \item April 2017. \textit{Comparative Study of Differentially Private Data Synthesis Methods}. Department of Mathematics and Statistics at University of Maryland - Baltimore County, Baltimore, MD.
    
% \newpage
\vspace{6pt}
\hspace{-0.30in}\underline{\textbf{\large Panels (Moderator)}}\normalsize   
    \item Aug. 2024. \textit{Data-Informed Policymaking: Statisticians and Data Scientists Building \& Communicating Evidence }. Joint Statistical Meetings, Portland, OR. \textbf{Session organizer.}
    
    \item April 2023. \textit{Leadership in Government}. COPSS-NISS Leadership Webinar Series, Urban Institute, Virtual.
    
    \item Jan. 2023. \textit{Funding Opportunities}. NISS IOF Workshop on Advancing Demographic Equity with Privacy-Preserving Methodologies, Urban Institute, Washington D.C.
    
    \item Nov. 2022. \textit{Current Challenges and Potential Future Work Panel}. National Institute of Statistical Science, Virtual.
    
    \item June 2022. \textit{Science and Technology Policy Panel}. Symposium on Data Science and Statistics, Pittsburgh, PA.
    
    \item Feb. 2022. \textit{Urban Institute Equity Dialogue with Fanta Traore}. Webinar hosted by the Urban Institute.
    
    \item June 2021. \textit{2020 Census}. Symposium on Data Science and Statistics, Virtual.
    
    \vspace{6pt}
% \newpage
\hspace{-0.30in}\underline{\textbf{\large Panels (Panelist)}}\normalsize
    \item Feb. 2023. \textit{Breaking the Economics Bubble: How Can We Make Research More Applied?} Federal Reserve System Research Assistant, Virtual.
    
    \item Dec. 2022. \textit{Data Infrastructure Issues for Evidence-Based Policy and Practice}. Federal Evaluation Forum at the Urban Institute, Virtual.
    
    \item April 2022. \textit{Writing and communicating well}. Rising Stars in Computational and Data Sciences Workshop.

    \item Feb. 2022. \textit{Differential Privacy and disparate impacts in downstream decisions and learning tasks}. Association for the Advancement of Artificial Intelligence Workshop of Privacy Preserving Artificial Intelligence.
    
    \item Nov. 2021. \textit{Panel Discussion About Careers in Industry and Government}. Electronic Undergraduate Statistics Research Conference, Virtual.

    \item May 2021. \textit{Career Advice Panel}. Department of Statistics, North Carolina State University, Virtual.
    
    \item April 2021. \textit{Think Tanks Panel}. Graduate Student Union Professional Development Series at University of Notre Dame, Virtual.
    
    \item April 2021. \textit{Judges Panel: The soft skills of data analytics}. DataFest at Bryant University, Virtual.
\end{etaremune}
