%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Media
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{etaremune}[topsep=0pt, itemsep=3pt, partopsep=0pt, parsep=0pt]

    \item Nov. 2023. Feature. \textit{JSM Session Touches on Equity}. Amstat News.
    
    \item Oct. 2023. Interview. \textit{Getting to Know the ASA's Government Employment Sector}. Amstat News.
    
    \item Feb. 2023. Interview. \textit{Interview: Claire McKay Bowen}. Significance.
    
    \item Jan. 2023. Interview. \textit{Rewards Points vs. Privacy}. Stats + Stories Podcast.
    
    \item Jan. 2023. Quote. \textit{And Just Like That, America Becomes More Rural}. Wall Street Journal Quote.
    
    \item Nov. 2022. Interview. \textit{Keeping Individual Data Private}. Stats + Stories Podcast.
    
    \item May 2022. Interview. \textit{The Data Privacy Scientist, Claire McKay Bowen}. Radiations.
    
    \item April 2022. Interview. \textit{Dr. Claire McKay Bowen}. The PolicyViz Podcast.
    
    \item April 2022. Interview. \textit{Ruobin Gong interviews Claire McKay Bowen}. Institute of Mathematical Statistics Bulletin.
    
    \item Feb. 2022. Interview. \textit{Can Third Graders Learn Data Science? These Researchers Say Yes}. EdSurge.
    
    \item Jan. 2022. Interview. \textit{ISU graduate writes book on data privacy}. Local News 8 in Idaho.
    
    \item Jan. 2022. Interview. \textit{Idaho State Alumna Authors Book on Data Privacy}. Idaho State University News.

    \item Aug. 2021. Interview. \textit{The Life of an ASA Conference Program Chair}. Practical Significance.    

    \item June 2021. Interview. \textit{Career Story}. Significance.
    
    \item May 2021. Feature. \textit{2021 COPSS Award Winners}. Amstat News.
    
    \item April 2021. Feature. \textit{People of Science Feature}. Science is US.
    
    \item April 2021. Interview. \textit{The Data Privacy Landscape is Changing}. Stats + Stories Podcast.
    
    \item Feb 2021. Interview. \textit{Privacy Talk with Claire McKay Bowen}. Privacy Talk Interview.

    \item March 2020. Feature. \textit{Celebrating Women in Statistics}. Women's History Month feature in Amstat News.

    \item March 2020. Interview. \textit{Data\@Urban Digital Discussions ft. Graham MacDonald and Claire Bowen}. Data\@Urban Digital Discussions, webinar hosted by the Urban Institute.
    
    \item Nov. 2019. Interview. \textit{Differential Privacy? w/ Dr. Claire McKay Bowen}. Data Science Imposters Podcast.
\end{etaremune}
