%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STEM K - 12 Service
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{High School Outreach} \hfill \textit{May 2022 \& 2023}\\
\textit{Speaker} - talk to AP statistics high school students about careers in statistics and working in public policy research. 
\outreachspace

\textbf{DataFest} \hfill \textit{March 2021, 2022, \& 2023}\\
\textit{Judge} - Evaluated the student team presentations for the ASA DataFest hosted by Bridgewater State University, Bryant University, UMass Dartmouth, and Stonehill College.
\outreachspace

\textbf{StatFest 2021} \hfill \textit{Sept. 2021}\\
\textit{Volunteer} - Spoke about how to network in a virtual environment.

\outreachspace
\textbf{Skype a Scientist} \hfill \textit{March 2021}\\
\textit{Speaker} - Led a virtual hands-on activity about how to use technology safely for the East Brunswick Brownie Troop for their Cybersecurity I: Basics badge.

\outreachspace
\textbf{StatFest 2020} \hfill \textit{Sept. 2020}\\
\textit{Volunteer} - Facilitated a roundtable on how to network in a virtual environment.

\outreachspace
\textbf{Digital Discussions: Data4Kids} \hfill \textit{May 2020}\\
\textit{Volunteer} - Presented a virtual hands-on activity about how to collect, visualize, and analyze data for primary and secondary level kids.

\outreachspace
\textbf{Adventures in Science} \hfill \textit{Feb. 2020}\\
\textit{Volunteer} - Presented a hands-on statistics experiment and analysis workshop for middle school students.

\outreachspace
\textbf{Julia Robinson Mathematics Festival} \hfill \textit{March 2019}\\
\textit{Volunteer} - Led the hexaflexagon workshop for middle school students.

\outreachspace
\textbf{Northern New Mexico Expanding Your Horizons} \hfill \textit{Oct. 2018}\\
\textit{Volunteer} - Presented a hands-on statistics experiment and analysis workshop for middle school girls.

\outreachspace
\textbf{St. Joseph County Public Library's Science Alive} \hfill \textit{Feb. 2014, 2015, 2016, \& 2018}\\
\textit{\href{http://sjcpl.lib.in.us/sciencealive/}{Volunteer}} - Created fun science hands-on activities for K-12 students such as digging for dinosaur bones at the annual Science Alive Event at the local library, where over 3,000 children learn how science is fun.

\outreachspace
\textbf{University of Notre Dame Expanding Your Horizons} \hfill \textit{April 2014, 2015, 2016, \& 2017}\\
\textit{\href{http://www.expandingyourhorizons.org/conferences/NotreDame/}{Volunteer}} - Provided insight on being a woman in science for the parents of middle school girls; Presented a data privacy workshop and probability hands-on science activities for middle school girls. 

\outreachspace
\textbf{University of Notre Dame Pi Day 5K} \hfill \textit{March 2015, 2016, \& 2017}\\
\textit{\href{http://www.awis.nd.edu/piday5k}{Co-Founder \& Organizer}} - Organized a 1 mile walk, 5K run, and 10K run as well as facilitated science demos and laboratory tours for the community to raise funds for the Boys and Girls Club, which raised over \$10,000.

% \vspace{2pt}
% \cventry{}{Organizer}{ACMS Department Graduate Student Seminars}{\textnormal{\textit{Aug. 2015 - March 2016}}}{}{\begin{itemize}
% \item Organize bimonthly seminars for the ACMS graduate students to share their research or techniques they have learned, creating a friendly environment for students to meet.\end{itemize}}

\outreachspace
\textbf{Girls on the Run Michiana} \hfill \textit{Jan. 2014 - May 2014}\\
\textit{\href{http://www.girlsontherunmichiana.org/}{Coach}} - Mentored and taught girls in middle school to "inspire [them] to be joyful, healthy, and confident using a fun, experience-based curriculum which creatively integrates running." - Girls on the Run

\outreachspace
\textbf{South Bend Community First Friday Event} \hfill \textit{March 2014 \& Feb. 2015}\\
\textit{\href{http://acms.nd.edu/news/47182-acms-first-friday-mad-about-science/}{Volunteer}} - Performed a probability hands-on activity called Monty Hall with the South Bend Community who attend the First Friday Event to learn more about mathematics and statistics.

\outreachspace
\textbf{Idaho National Laboratory's My Amazing Future Program} \hfill \textit{May 2013}\\
\textit{\href{https://inlportal.inl.gov/portal/server.pt?open=514&objID=1269&mode=2&featurestory=DA_575131}{Instructor}} - Encouraged dozens of young girls to pursue careers in STEM through fun physics demonstrations. 

\outreachspace
\textbf{Idaho State University Physics Department Demonstration Shows} \hfill \textit{Aug. 2008 - May 2013}\\
\textit{Demonstration Assistant} - Assisted in presenting educational demonstration shows for K-12 students throughout Idaho, Nevada, and Utah; reaching out to thousands of children to engage them in science.

\outreachspace
\textbf{Southeastern Idaho Mathematics Counts} \hfill \textit{Feb. 2009, 2010, 2011, 2012, \& 2013}\\
\textit{Set-Up/Grader/Judge} - Assisted the event by setting-up, grading, and judging.

\outreachspace
\textbf{Future Faces of Physics Award Project} \hfill \textit{Aug. 2012 - Nov. 2012}\\
\textit{\href{http://www.spsnational.org/programs/awards/2012/FFoP/ffop_recipients.htm}{Instructor}} - aught a local Native American fourth grade class how to design and build egg launchers; Guided the students in participating at a local competition.

\outreachspace
\textbf{Idaho State University - Pocatello, Dept. of Physics} \hfill \textit{June 2011 \& 2012}\\
\textit{QuarkNet Assistant} - Assisted the instructor in educating Idaho Teachers how to teach certain areas of STEM; Built the science demonstrations and tools the Idaho Teachers used to help understand science concepts.

\outreachspace
\textbf{Annual Society of Physics Students ISU Chapter Pumpkin Chuck} \hfill \textit{Oct. 2009, 2010, \& 2011}\\
\textit{\href{http://www.idahostatejournal.com/news/local/article_845b6364-cc47-11de-b59c-001cc4c002e0.html}{Head Organizer}} - Organized the event for local high schools and colleges to compete by designing trebuchets or catapults that can fling pumpkins as far and accurate as possible.

\outreachspace
\textbf{Annual Society of Physics Students Haunted Laboratory} \hfill \textit{Oct. 2008, 2009, 2010, \& 2011}\\
\textit{\href{http://www.isu.edu/headlines/?p=3408}{Head Organizer/Volunteer}} - Assisted in setting up the Haunted Laboratory to scare children with spooky physics and taught them the science of light and illusion; Collaborated with Kiwanis Club in expanding the Haunted Laboratory to a warehouse to accommodate more children.

\outreachspace
\textbf{Annual Idaho State University Science Olympics} \hfill \textit{March 2010 \& 2011}\\
\textit{Volunteer} - Judged how elementary school students tackled various science competitions and challenges such as building circuits or creating wooden airplanes.

\outreachspace
\textbf{Annual Society of Physics Students ISU Chapter Science Day in the Mall} \hfill \textit{March 2009 \& 2011}\\
\textit{\href{http://m.idahostatejournal.com/news/local/idaho-state-university-physics-club-receives-national-award/article_1823c468-8600-11e2-94b3-0019bb2963f4.html?mode=image&photo=0}{Head Organizer/Volunteer}} - Celebrated Einstein's Birthday and Pi Day with liquid nitrogen ice cream as well as electricity and magnetism activities for children, reaching hundreds of locals.

\outreachspace
\textbf{Idaho Museum of Natural History at Idaho State University} \hfill \textit{Jan. 2009 - May 2010}\\
\textit{\href{http://imnh.isu.edu/home/index.php/science-trek/}{Science Trek \& Science Snacks Instructor}} - Taught children STEM concepts in physics (such as rockets and optics) through physics demonstrations and hands on activities.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Other Activities
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Non-Profit Activities}

% \textbf{Aquatomics} - USA Masters Swim Group in Los Alamos, NM

% \textbf{Santa Fe Road Riders} - Road Cycling Club in Santa Fe, NM 

% \textbf{Triatomics} - Triathlon Club in Los Alamos, NM

