%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Publications
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent\underline{\textbf{Book(s)}}
\begin{etaremune}[topsep=0pt, itemsep=0pt, partopsep=0pt, parsep=0pt]
  \item \textbf{Bowen, CMK.} ``Protecting Your Privacy in a Data-Driven World.'' (Nov. 2021) \textit{Routledge-CRC Press}, American Statistical Association-CRC Series on Statistical Reasoning in Science and Society.
\end{etaremune}

\vspace{6pt}
\noindent\underline{\textbf{Refereed Publications}}
\vspace{4pt}
\begin{etaremune}[topsep=0pt, itemsep=5pt, partopsep=0pt, parsep=0pt]
    \item Williams, A. R., and \textbf{Bowen, CMK}. (2023) ``The Promise and Limitations of Formal Privacy.'' \textit{WIREs Computational Statistics}. e1615. doi.org/10.1002/wics.1615
    
    \item \textbf{Bowen, CMK.}, Bryant, V., Burman, L., Khitatrakun, S., McClelland, R., Mucciolo, L., Pickens, M., and Williams, A. (2022) ``Synthetic Individual Income Tax Data: Promises and Challenges.'' \textit{National Tax Journal}, 75(4), 767-790.
    
    \item \textbf{Bowen, CMK.}, Bryant, V., Burman, L., Czajka, J., Khitatrakun, S., MacDonald, G., McClelland, R., Mucciolo, L., Pickens, M., Ueyama, K., Williams, A., Wissoker, D., and Zwiefel, N. (2022) ``Synthetic Individual Income Tax Data: Methodology, Utility, and Privacy Implications.'' \textit{Privacy in Statistical Databases: International Conference, PSD 2022, Paris, France, September 21–23, 2022}, Proceedings (pp. 191-204). Cham: Springer International Publishing.
    
    \item Youngs, I., Dick, C., Prevost, R., and \textbf{Bowen, CMK}. (2022). ``Expectations for the 2020 Decennial Census and How They Stood Up to Scrutiny.'' \textit{International Journal of Population Data Science}, 7(3).
    
    \item Liu, F., Eugenio, E., Jin, I., and \textbf{Bowen, CMK}. (2022) ``Differentially Private Synthesis and Sharing of Network Data via Bayesian Exponential Random Graph Models.'' \textit{Journal of Survey Statistics and Methodology}, 10(3), 753-784. doi: 10.1093/jssam/smac017
    
    \item Garfinkel, S. and \textbf{Bowen, CMK} (2022) ``Preserving Privacy While Sharing Data.'' \textit{MIT Sloan Management Review}, 63 (3), 1-4.
    
    \item \textbf{Bowen, CMK} and Garfinkel, S. (2021) ``The Philosophy of Differential Privacy.'' \textit{Notices of the American Mathematical Society}, 68(10), pages 1727-1739. doi: 10.1090/noti2363
    
    \item \textbf{Bowen, CMK.}, Liu, F., Su, B. (2021) ``Differentially Private Data Release via Statistical Election to Partition Sequentially.'' \textit{METRON}, Issue 79, pages 1-31. doi: 10.1007/s40300-021-00201-0
    
    \item \textbf{Bowen, CMK.} and Snoke, J. (2021) ``Comparative Study of Differentially Private Synthetic Data Algorithms from the NIST PSCR Differential Privacy Synthetic Data Challenge.'' \textit{Journal of Privacy and Confidentiality}, 11(1). doi: 10.29012/jpc.748
    
    \item Snoke, J., and \textbf{Bowen, CMK.} (2020) ``How Statisticians Should Grapple with Privacy in a Changing Data Landscape.'' \textit{CHANCE}, 33(4), pages 6-13. doi: 10.1080/09332480.2020.1847947
    
    \item \textbf{Bowen, CMK.}, Bryant, V., Burman, L., Khitatrakun, S., McClelland, R., Stallworth, P., Ueyama, K., Williams, A. (2020) ``A Synthetic Supplemental Public Use File of Low-Income Information Return Data: Methodology, Utility, and Privacy Implications.'' \textit{International Conference on Privacy in Statistical Databases}, pages 257-270. Springer, Cham.
    
    \item Liu, F., Eugenio, E., Jin, I., and \textbf{Bowen, CMK}. (2020) ``Differentially Private Generation of Social Networks via Exponential Random Graph Models.'' \textit{Proceedings of 2020 IEEE 44th Annual Computers, Software, and Applications Conference (COMPSAC)}, pages 1695-1700. doi: 10.1109/COMPSAC48688.2020

    \item \textbf{Bowen, CMK.} and Liu, F. (2020) ``Comparative Study of Differentially Private Data Synthesis Methods.'' \textit{Statistical Science}, 35(2), pages 280-307.

    \item \textbf{Bowen, CMK.}, DeBardeleben, N., Blanchard, S., Anderson-Cook, C. (2019) ``Do Solar Proton Events Reduce the Number of Faults in Supercomputers?: A Comparative Analysis of Faults during and without Solar Proton Events." \textit{2019 IEEE International Reliability Physics Symposium}.

    \item \textbf{Bowen, CMK.} and Eugenio, E. (2017) ``Where's Wenda:  An Activity on Teaching Middle School Students Data Privacy.'' \textit{Statistics Teacher}, Issue No. 1.
    
    \item Myers, K., Lawrence, E., Fugate, M., \textbf{Bowen, CMK.}, Ticknor, L., Woodring, J., Wendelberger, J., Ahrens, J. (2016) ``Partitioning a Large Simulation as It Runs.'' \textit{Technometrics}, 58(3), pages 329-340. doi: 10.1080/00401706.2016.1158740

    \item \textbf{Bowen, CMK.}, Liu, F., \& Wheeler, J. (2015) ``Are More of My Patients Developing Side Effects than Expected.'' \textit{Practical Radiation Oncology}, 5(3), pages e255-e261.\\
    doi: 10.1016/j.prro.2014.10.007
\end{etaremune}

\vspace{4pt}
% \newpage
\noindent\underline{\textbf{Under Review/Preprint}}
\begin{etaremune}[topsep=0pt, itemsep=4pt, partopsep=0pt, parsep=0pt]  
    \item \textbf{Bowen, CMK}. ``Response to Citro et al. and the greater statistical community''
    
    \item Snoke, J., \textbf{Bowen, CMK}., Williams, A. R., and Barrientos, A. F. ``Incompatibilities Between Current Practices in Statistical Data Analysis and Differential Privacy''
    
    \item Williams, A. R., Snoke, J., \textbf{Bowen, CMK}., and Barrientos, A. F. ``Disclosing Economists' Privacy Perspectives: A Survey of American Economic Association Members on Differential Privacy and Data Fitness for Use Standards.''
    
    \item Barrientos, A. F., Williams, A. R., Snoke, J., and \textbf{Bowen, CMK}. ``A Feasibility Study of Differentially Private Summary Statistics and Regression Analyses for Administrative Tax Data.'' arXiv:2110.12055
\end{etaremune}

% \newpage
\vspace{4pt}
\noindent\underline{\textbf{Articles, Editorials, and Other Publications not peer reviewed}}
\vspace{4pt}
\begin{etaremune}[topsep=0pt, itemsep=5pt, partopsep=0pt, parsep=0pt]
    \item Ko, R., Balu, R., \textbf{Bowen, CMK}., DeRuiter-Williams, D., Frederick, R., Pindus, N. M., ... and Rodríguez, S. T. (2023). ``Public Comment on initial proposals from the Federal Interagency Technical Working Group on Race and Ethnicity Standards for revising OMB’s 1997 Statistical Policy Directive No. 15.'' \textit{Urban Institute}.

    \item \textbf{Bowen, CMK}. and Snoke, J. (2023) ``Do No Harm Guide: Applying Equity Awareness in Data Privacy Methods.'' \textit{Urban Institute}.

    \item \textbf{Bowen, CMK}. Williams, A. R., and Pickens, M. (2022) ``Decennial Disclosure: An Explainer on Formal Privacy and the TopDown Algorithm.'' \textit{Urban Institute}.
    
    \item Morrison, G., and \textbf{Bowen, CMK}. (2022) ``Internet First or Internet Choice? Identifying Factors to Predict Low Self-Response Rates on the 2020 Census.'' \textit{Urban Institute}.
    
    \item Barrientos, A. F., Williams, A. R., Snoke, J., and \textbf{Bowen, CMK}. (2021) ``Differentially Private Methods for Validation Servers: A Feasibility Study of Differentially Private Summary Statistics and Regression Analyses for Administrative Tax Data.'' \textit{Urban Institute}.
    
    \item Taylor, S., MacDonald, G., Ueyama, K., and \textbf{Bowen, CMK.} (2021) ``A Privacy-Preserving Validation Server Prototype.'' \textit{Urban Institute}.
        
    \item \textbf{Bowen, CMK.} (2021) ``Personal Privacy and the Public Good: Balancing Data Privacy and Data Utility.'' \textit{Urban Institute}.
    
    \item \textbf{Bowen, CMK.}, Narayanan, A., Scally, C. (2021) ``Using Differential Privacy to Advance Rural Economic Development: Applying Data Privacy and Confidentiality Methods to Industry Employment Data.'' \textit{Urban Institute}.
    
    \item \textbf{Bowen, CMK.}, Burman, L., Khitatrakun, S., MacDonald, G., McClelland, R., Stallworth, P., Ueyama, K., Williams, A., Zwiefel, N. (2020) ``A Synthetic Supplemental Public-Use File of Low-Income Information Return Data: Methodology, Utility, and Privacy Implications.'' \textit{Urban Institute}
    
    \item \textbf{Bowen, CMK.} (2016) ``NSF GRIP Report: American Community Survey Simulation Study." \textit{U.S. Census Bureau}.  
\end{etaremune}

\vspace{4pt}
\noindent\underline{\textbf{Blogs and Professional Service Publications}}
\vspace{4pt}
\begin{etaremune}[topsep=0pt, itemsep=5pt, partopsep=0pt, parsep=0pt]
    \item \textbf{Bowen, CMK}. and Snoke, J. (2023) ``Applying Equity Awareness in Statistical Data Privacy Takes a Village'' \textit{Amstat News}, May Issue.
    
    \item Auerbach, J., \textbf{Bowen, CMK.}, Citro, C., Pierson, S., and Potok, N. (2023) ``ASA, GMU Team on Project to Assess Health of Federal Statistical Agencies'' \textit{Amstat News}, April Issue.
    
    \item Messner, M. and \textbf{Bowen, CMK.} (2022) ``Spotlight on the Government Statistics Section of the American Statistical Association.'' \textit{CHANCE}, 35(3), pages 4-8.
    
    \item Hu, J. and \textbf{Bowen, CMK.} (2022) ``Prescribing Privacy: Human and Computational Resource Limitations and What Statisticians and Data Scientists Can Do.'' \textit{Amstat News}, September Issue.
    
    \item \textbf{Bowen, CMK.} (2022) ``SDSS 2022: Connecting and Influencing Our Society.'' \textit{Amstat News}, August Issue.
    
    \item Schwabish, J. and \textbf{Bowen, CMK.} (2022) ``Data4Kids: A Collaborative Project to Teach Kids about Data.'' \textit{Nightingale}.
    
    \item \textbf{Bowen, CMK.} and Schwabish, J. (2022) ``How Data4Kids Helps Students Log on to Learn.'' \textit{Data@Urban}.

    \item \textbf{Bowen, CMK.} (2022) ``Beyond Big Data: Supporting Students and Early-Career Professionals.'' \textit{Amstat News}, February Issue.
    
    \item \textbf{Bowen, CMK.} (2022) ``The Art of Data Privacy.'' \textit{Significance Magazine}, February Issue.
    
    \item \textbf{Bowen, CMK.} (2021) ``Analyzing the Quality of 2020 Census: Understanding the US Population Puzzle.'' \textit{Data@Urban}.

    \item \textbf{Bowen, CMK.} (2021) ``Claire McKay Bowen Talks Data Privacy.'' \textit{Amstat News}, December Issue.
    
    \item \textbf{Bowen, CMK.} (2021) ``Utility Metrics for Differential Privacy: No One-Size-Fits-All.'' \textit{Differential Privacy: NIST Blog Series}.
    
    \item \textbf{Bowen, CMK.} (2021) ``Data Science and Statistics Influencing Science, Technology, and Society.'' \textit{Amstat News}, October Issue.
    
    \item \textbf{Bowen, CMK.} (2021) ``Sailing Your Own Path: An Interview with Jeri Mulrow.'' \textit{Amstat News}, September Issue.

    \item \textbf{Bowen, CMK.} (2021) ``Star Statisticians Offer Career Advancement Advice.'' \textit{Amstat News}, September Issue.    
    
    \item Martinez, W., \textbf{Bowen, CMK.}, LaLonde, D. (2021) ``Beyond Big Data: Shaping the Future - SDSS 2021.'' \textit{Amstat News}, August Issue.   
    
    \item \textbf{Bowen, CMK.} and Mannshardt, E. (2021) ``Committee on Career Development Announces Initiative Lineup.'' \textit{Amstat News}, June Issue.

    \item \textbf{Bowen, CMK.} (2021) ``How data privacy methods can hide the real data story.'' \textit{International Statistical Institute}, Statisticians React to the News.
    
    \item \textbf{Bowen, CMK.}, Williams, A., and Narayanan, A. (2021) ``To Advance Racial Equity, Releasing Disaggregated Data while Protecting Privacy Will Be Key.'' \textit{Urban Wire}. 
    
    \item Brown, S, MacDonald, G., and \textbf{Bowen, CMK.} (2021) ``How the Federal Government Can Use Data to Make the Most of the Executive Order on Racial Equity.'' \textit{Urban Wire}. 

    \item \textbf{Bowen, CMK.} (2020) ``To bike or not to bike...in a group?'' \textit{International Statistical Institute}, Statisticians React to the News.

    \item \textbf{Bowen, CMK.} (2020) ``My ASA Story.'' \textit{Amstat News}, December Issue.

    \item Chase, E., \textbf{Bowen, CMK.}, Director, H., Baladandayuthapani, V. and Pierson, S. (2020) ``Panel Shares Advice on Applying for NSF Fellowships.'' \textit{Amstat News}, November Issue.

    \item \textbf{Bowen, CMK.} and Mannshardt, E. (2020) ``Committee on Career Development Holds Virtual Office Hours with Experts.'' \textit{STAT tr@k News}, June Issue.

    \item \textbf{Bowen, CMK.} and Mannshardt, E. (2020) ``Reaching Your Networking Peak: A Guided Networking Session at JSM.'' \textit{Amstat News}, April Issue.
    
    \item \textbf{Bowen, CMK.} (2020) ``Will the Census Bureau's data privacy efforts erase rural America?'' \textit{Urban Wire}. 
    
    \item Snoke, J. and \textbf{Bowen, CMK.} (2019) ``Differential Privacy: What Is It?'' \textit{Amstat News}, March Issue.
\end{etaremune}