%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Presentations
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{etaremune}[topsep=0pt, itemsep=4pt, partopsep=0pt, parsep=0pt]
    \item April 2024. \textit{Navigating Data Privacy: Balancing Confidentiality and Accessibility in a Data-Driven World}. Department of Labor CEO Seminar, Virtual.
    
    \item April 2024. \textit{Urban Institute's Data Governance and Privacy Work: Ensuring all people are responsibly represented in data}. PETs SubIPC, Virtual.

    \item March 2024. \textit{Key Considerations in Data Synthesis and Its Application to Criminal Cases in State Courts}. Bureau of Justice Statistics, Virtual.
    
    \item Oct. 2023. \textit{Data Privacy Considerations for Data Disaggregation}. Disaggregation Nation: Data Equity Summit, Washington, DC.
    
    \item Sept. 2023. \textit{Assessing the Health of the Federal Statistical Agencies}. Council of Professional Associations on Federal Statistics Quarterly Meeting, Virtual.

    \item June 2023. \textit{Do No Harm Guide: Applying Equity Awareness in Data Privacy Methods}. Mercury Project Virtual Convening, Virtual.
    
    \item March 2023. \textit{Safely Expanding Access to Administrative Tax Data}. California Labor and Workforce Development Agency, Virtual.
    
    \item March 2023. \textit{Discussant: 2030 Federal Register Notice Comments / Feedback - Group 2}. Census Scientific Advisory Committee Virtual Meeting, Spring 2023.
    
    \item Sept. 2022. \textit{Improving Disclosure Protections on the Current Population Survey Public Use File: Discussant Comments}. Census Scientific Advisory Committee Virtual Meeting, Fall 2022.
    
    \item July 2022. \textit{Data Privacy and Public Policy at the Urban Institute.} FTAC Adoption Subgroup.
    
    \item May 2022. \textit{Safely Expanding Access to Administrative Tax Data for Better Public Policymaking.} Urban Institute's Board of Trustees.
    
    \item April 2022. \textit{Privacy threats and re-identification risks.} Advisory Committee on Data for Evidence Building Technical Infrastructure Subcommittee Meeting.
    
    \item March 2022. \textit{Data4Kids: Virtually Teaching Kids about Data Science.} South Big Data Hub S.E.E.D.S. Panel for the Funders and Grant Recipients.
    
    \item Oct. 2021. \textit{Synthetic Public Use File (SynPUF) and Future Work.} Administrative Tax Data Project for the Advisory Board, Funders, and Guests.
    
    \item July 2021. \textit{Validation Server Project: Advisory Board Meeting.} Validation Server Project for the Advisory Board, Funders, and Guests.
    
    \item July 2021. \textit{Expanding Access to Confidential Administrative Tax Data with Synthetic Data and Validation Server.} Sloan Foundation, Actuate, Georgetown University, the University of Illinois at Urbana-Champaign, and the Urban Institute
    
    \item April 2021. \textit{Creating a Synthetic Public Use File.} Administrative Tax Data Project for the Internal Revenue Service Statistics of Income Division.

    \item Dec. 2020. \textit{Using Differential Privacy to Advance Rural Economic Development: Applying Data Privacy and Confidentiality Methods to Industry Employment Data.} Fleishman Award Project for the Bureau of Labor Statistics.
    
    \item Dec. 2020. \textit{Validation Server Project: Advisory Board Meeting.} Validation Server Project for the Advisory Board, Funders, and Guests.
    
    \item Sept. 2020. \textit{Validation Server Project - Kickoff Meeting.} Validation Server Project for the Internal Revenue Service Statistics of Income Division and National Science Foundation.
    
    \item July 2020. \textit{Creating a Synthetic Public Use File of Nonfilers.} Administrative Tax Data Project for the Advisory Board, Funders, and Guests.
    
    \item Oct. 2019. \textit{Functional Data Analysis for Iterative Design.} Laboratory Directed Research \& Development Project for the Review Committee and Guests.
\end{etaremune}
